---
title: "Business Continuity Plan — Broadcast Facility & Staff"
subtitle: "`r params$asset_name`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
geometry: margin=1in
fontsize: 11pt
params:
  username: "user"
  asset_name: "Broadcast Facility"
  address: "123 Main St, Gainesville, FL 32601"
  lat: 29.65
  lon: -82.33
  zip: "32601"
  city: "Gainesville"
  nearest_airport_icao: "KGNV"
  nearest_airport_name: "Gainesville Regional Airport"
  asset_type: "Radio Station"
  notes: ""
  mongo_uri: "mongodb://localhost:27017/"
  days_back: 30
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", out.width = "90%")
suppressPackageStartupMessages({
  library(mongolite); library(dplyr); library(ggplot2)
  library(knitr); library(kableExtra); library(lubridate)
})
FPREN_BLUE <- "#003087"
start_date <- Sys.time() - days(params$days_back)
mongo_uri  <- params$mongo_uri
safe_mongo <- function(collection, db = "weather_rss") {
  tryCatch(mongo(collection=collection, db=db, url=mongo_uri), error=function(e) NULL)
}
```

\definecolor{fprenblue}{HTML}{003087}

\begin{center}
\textcolor{fprenblue}{\rule{\linewidth}{2pt}}
\vspace{4pt}
{\Large\textbf{\textcolor{fprenblue}{FPREN --- Florida Public Radio Emergency Network}}}\\
{\large\textbf{Broadcast Facility \& Staff Business Continuity Plan}}\\
\vspace{4pt}
\textcolor{fprenblue}{\rule{\linewidth}{1pt}}
\end{center}

\vspace{6pt}

```{r cover-table, results='asis'}
cover <- data.frame(
  Field = c("Facility Name","Asset Type","Address","Coordinates",
            "Nearest City","Nearest Airport","Prepared For",
            "Report Generated","Days Covered"),
  Value = c(params$asset_name, params$asset_type, params$address,
            paste0(params$lat, " N, ", abs(params$lon), " W"),
            params$city,
            paste0(params$nearest_airport_icao, " -- ", params$nearest_airport_name),
            params$username,
            format(Sys.time(), "%Y-%m-%d %H:%M ET"),
            paste0(params$days_back, " days")),
  stringsAsFactors = FALSE
)
kable(cover, col.names=NULL, booktabs=TRUE, linesep="") %>%
  kable_styling(latex_options="hold_position", full_width=FALSE) %>%
  column_spec(1, bold=TRUE, color=FPREN_BLUE, width="6cm") %>%
  column_spec(2, width="9cm")
```

> **Confidential** -- For authorized FPREN broadcast personnel only.

\newpage

# Executive Summary

```{r exec-summary}
alerts_col    <- safe_mongo("nws_alerts")
recent_alerts <- tryCatch({
  if (is.null(alerts_col)) stop()
  q <- sprintf('{"$or":[{"area_desc":{"$regex":"%s","$options":"i"}},{"counties":{"$regex":"%s","$options":"i"}}]}',
               params$city, params$city)
  r <- alerts_col$find(q, fields='{"event":1,"severity":1,"urgency":1,"sent":1,"expires":1,"_id":0}')
  alerts_col$disconnect(); r
}, error=function(e) { tryCatch(alerts_col$disconnect(), error=function(e2) NULL); data.frame() })

n_alerts  <- nrow(recent_alerts)
n_extreme <- if (n_alerts > 0 && "severity" %in% names(recent_alerts))
               sum(tolower(recent_alerts$severity) %in% c("extreme","severe"), na.rm=TRUE) else 0
alert_risk <- if (n_extreme >= 3) "HIGH" else if (n_extreme >= 1 || n_alerts >= 5) "MODERATE" else "LOW"

wx_col  <- safe_mongo("weather_history")
wx_hist <- tryCatch({
  if (is.null(wx_col)) stop()
  r <- wx_col$find(
    sprintf('{"icao":"%s","timestamp":{"$gte":"%s"}}', params$nearest_airport_icao,
            format(start_date, "%Y-%m-%dT%H:%M:%SZ")),
    fields='{"temp_f":1,"wind_speed":1,"flight_cat":1,"visibility":1,"_id":0}')
  wx_col$disconnect(); r
}, error=function(e) { tryCatch(wx_col$disconnect(), error=function(e2) NULL); data.frame() })

max_wind <- if (nrow(wx_hist) > 0 && "wind_speed" %in% names(wx_hist))
              max(wx_hist$wind_speed, na.rm=TRUE) else NA_real_
n_ifr    <- if (nrow(wx_hist) > 0 && "flight_cat" %in% names(wx_hist))
              sum(wx_hist$flight_cat %in% c("IFR","LIFR"), na.rm=TRUE) else 0
wx_risk  <- if (!is.na(max_wind) && (max_wind > 40 || n_ifr > 10)) "HIGH" else
            if (!is.na(max_wind) && (max_wind > 25 || n_ifr > 3))  "MODERATE" else "LOW"

traffic_col <- safe_mongo("fl_traffic")
traffic_df  <- tryCatch({
  if (is.null(traffic_col)) stop()
  r <- traffic_col$find(
    sprintf('{"county":{"$regex":"%s","$options":"i"}}', params$city),
    fields='{"type":1,"severity":1,"is_full_closure":1,"road":1,"description":1,"_id":0}')
  traffic_col$disconnect(); r
}, error=function(e) { tryCatch(traffic_col$disconnect(), error=function(e2) NULL); data.frame() })
n_closures   <- if (nrow(traffic_df) > 0 && "is_full_closure" %in% names(traffic_df))
                  sum(traffic_df$is_full_closure == TRUE, na.rm=TRUE) else 0
traffic_risk <- if (n_closures >= 2) "HIGH" else
                if (n_closures >= 1 || nrow(traffic_df) > 5) "MODERATE" else "LOW"

overall_risks <- c(alert_risk, wx_risk, traffic_risk)
overall_risk  <- if (any(overall_risks == "HIGH")) "HIGH" else
                 if (any(overall_risks == "MODERATE")) "MODERATE" else "LOW"
```

This plan covers **`r params$asset_name`** broadcast operations at `r params$address`. It addresses equipment protection, on-air continuity, staff safety, and FCC obligations during weather emergencies. Analysis period: `r params$days_back` days ending `r format(Sys.Date(), "%B %d, %Y")`.

```{r risk-table, results='asis'}
risk_df <- data.frame(
  Category = c("Weather / Antenna Risk","NWS Alert Activity",
               "Road Access / Staff Commute","Overall Risk Level"),
  Level    = c(wx_risk, alert_risk, traffic_risk, overall_risk),
  Detail   = c(
    if (!is.na(max_wind)) paste0("Max wind: ", round(max_wind,1), " mph; IFR/LIFR hours: ", n_ifr)
    else "No weather history",
    paste0(n_alerts, " alerts; ", n_extreme, " Extreme/Severe"),
    paste0(n_closures, " full road closures; ", nrow(traffic_df), " incidents in county"),
    paste0(params$days_back, "-day combined assessment")
  ),
  stringsAsFactors=FALSE
)
kable(risk_df, col.names=c("Risk Category","Level","Detail"), booktabs=TRUE, linesep="") %>%
  kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
  column_spec(2, bold=TRUE,
    color=ifelse(risk_df$Level=="HIGH","red",ifelse(risk_df$Level=="MODERATE","orange","#2e7d32")))
```

`r if (nchar(params$notes) > 0) paste0("**Notes:** ", params$notes)`

\newpage

# Broadcast Equipment Continuity

## Primary Systems Checklist

```{r equipment-checklist, results='asis'}
equip <- data.frame(
  System = c(
    "Primary Transmitter","Backup/Auxiliary Transmitter",
    "Icecast Streaming Server","MongoDB Database Server",
    "UPS (Uninterruptible Power Supply)","Generator (Diesel/NG)",
    "Antenna System / Tower","Studio Mixing Console",
    "Piper TTS Engine","ElevenLabs API Credential",
    "Internet Circuit (Primary)","Internet Circuit (Backup)",
    "FPREN Icecast Port 8000","All 9 Zone Mounts Live",
    "NWS IPAWS Feed Active","FL511 Traffic Feed Active"
  ),
  `Verify Before Storm` = rep("[ ]", 16),
  `After Event Check`   = rep("[ ]", 16),
  `Notes / Status`      = c(
    "Check TX power output & SWR",
    "Confirm automatic failover enabled",
    "Verify all 9 mounts streaming",
    "Confirm mongod service running; backup current",
    "Test load transfer; check battery health",
    "Fuel level; oil; coolant; test run 30 min",
    "Inspect for physical damage; guy wires",
    "Console power; backup console available?",
    "Voice model path; GPU/CPU allocation",
    "Key valid; test with one critical alert",
    "Speed test; ISP contact on file",
    "Cellular/satellite fallback ready",
    "curl http://localhost:8000/status-json.xsl",
    "sudo systemctl list-units | grep stream",
    "sudo systemctl status beacon-ipaws-fetcher",
    "sudo systemctl status beacon-extended-fetcher"
  ),
  stringsAsFactors=FALSE
)
kable(equip, booktabs=TRUE, linesep="",
      col.names=c("System / Component","Before Storm","After Event","Notes")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="4.5cm") %>%
  column_spec(2, width="2cm") %>%
  column_spec(3, width="2cm") %>%
  column_spec(4, width="6cm")
```

## On-Air Continuity Options

```{r continuity-options, results='asis'}
cont <- data.frame(
  Scenario = c(
    "Primary studio loss","Transmitter failure","Internet outage",
    "Generator failure","Total facility loss"
  ),
  Action = c(
    "Switch to auxiliary/remote studio; activate pre-recorded emergency playlist",
    "Switch to backup TX; notify UF IT and tower crew",
    "Fall back to cellular hotspot; reduce stream bitrate to 64 kbps",
    "Transfer to UPS; start backup generator; reduce non-essential loads",
    "Activate remote broadcast from designated alternate site; notify FEMA EAS"
  ),
  Owner = c("Engineer on-call","RF Engineer","Admin","Facilities","Station Manager"),
  stringsAsFactors=FALSE
)
kable(cont, booktabs=TRUE, linesep="", col.names=c("Failure Scenario","Continuity Action","Owner")) %>%
  kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="4cm") %>%
  column_spec(2, width="9cm") %>%
  column_spec(3, width="3cm")
```

\newpage

# Staff Safety & Notification

## Staff Emergency Roles

```{r staff-roles, results='asis'}
roles <- data.frame(
  Role = c(
    "Station Manager","Chief Engineer","On-Air Talent","Production Staff",
    "IT / Systems Admin","Security / Facilities"
  ),
  Responsibility = c(
    "Activate BCP; communicate with UF administration; FCC EAS coordination",
    "Assess and restore transmitter, antenna, generator, and Icecast systems",
    "Maintain continuous broadcast; deliver NWS/IPAWS emergency messages",
    "Queue emergency playlist; manage pre-recorded content; assist engineer",
    "Monitor MongoDB, systemd services, network, and remote access",
    "Secure building; manage access; coordinate with campus police"
  ),
  `Shelter in Place` = c("Yes","Yes","Yes","Optional","Optional","Yes"),
  `Evacuate if Ordered` = rep("Yes", 6),
  stringsAsFactors=FALSE
)
kable(roles, booktabs=TRUE, linesep="",
      col.names=c("Role","Primary Responsibility","Shelter in Place","Evacuate if Ordered")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="3.5cm") %>%
  column_spec(2, width="8cm")
```

## Staff Accountability Checklist

Before evacuation or shelter-in-place:

1. **Broadcast Engineer** confirms all systems on backup power and streaming normally.
2. **Station Manager** activates automated emergency playlist if staff must evacuate.
3. **IT Admin** enables remote monitoring and VPN access for off-site management.
4. All staff check in via designated text/radio channel within **30 minutes** of activation.
5. Head count confirmed — no staff left in hazard zone without clearance.

\newpage

# Weather Risk Assessment

Historical data from **`r params$nearest_airport_icao`** (`r params$nearest_airport_name`), last `r params$days_back` days.

```{r weather-analysis, results='asis', fig.height=3.2}
if (nrow(wx_hist) == 0) {
  cat("> **No weather history available** for this station.\n")
} else {
  avg_temp  <- round(mean(wx_hist$temp_f, na.rm=TRUE), 1)
  avg_wind  <- if ("wind_speed" %in% names(wx_hist))
                 round(mean(wx_hist$wind_speed, na.rm=TRUE), 1) else NA
  max_wind2 <- if ("wind_speed" %in% names(wx_hist))
                 round(max(wx_hist$wind_speed, na.rm=TRUE), 1) else NA
  n_vfr  <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat=="VFR",  na.rm=TRUE) else 0
  n_mvfr <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat=="MVFR", na.rm=TRUE) else 0
  n_ifr2 <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat=="IFR",  na.rm=TRUE) else 0
  n_lifr <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat=="LIFR", na.rm=TRUE) else 0

  wx_stats <- data.frame(
    Metric = c("Average Temperature","Max Wind Speed","Avg Wind Speed",
               "VFR Hours","MVFR Hours","IFR Hours","LIFR Hours",
               "Antenna Wind Load Risk"),
    Value  = c(paste0(avg_temp," F"),
               if (!is.na(max_wind2)) paste0(max_wind2," mph") else "N/A",
               if (!is.na(avg_wind)) paste0(avg_wind," mph") else "N/A",
               n_vfr, n_mvfr, n_ifr2, n_lifr,
               if (!is.na(max_wind2) && max_wind2 > 50) "HIGH -- inspect guy wires"
               else if (!is.na(max_wind2) && max_wind2 > 35) "MODERATE -- monitor tower"
               else "LOW"),
    stringsAsFactors=FALSE
  )
  print(
    kable(wx_stats, col.names=c("Metric","Value"), booktabs=TRUE, linesep="") %>%
      kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
      column_spec(1, width="7cm") %>% column_spec(2, width="5cm")
  )

  if ("flight_cat" %in% names(wx_hist) && nrow(wx_hist) > 0) {
    cat_counts <- wx_hist %>% filter(!is.na(flight_cat)) %>%
      group_by(flight_cat) %>% summarise(n=n(), .groups="drop") %>%
      mutate(flight_cat=factor(flight_cat, levels=c("VFR","MVFR","IFR","LIFR")))
    cat_colors <- c(VFR="#0077aa", MVFR="#f0c030", IFR="#e07020", LIFR="#cc2222")
    print(
      ggplot(cat_counts, aes(x=flight_cat, y=n, fill=flight_cat)) +
        geom_col(width=0.6) + scale_fill_manual(values=cat_colors, guide="none") +
        labs(title=paste0("Flight Category Distribution -- ", params$nearest_airport_icao),
             x="Category", y="Hours") +
        theme_minimal(base_size=11) +
        theme(plot.title=element_text(color=FPREN_BLUE, face="bold"))
    )
  }
}
```

\newpage

# Recent NWS Alert History

```{r alerts-section, results='asis'}
if (nrow(recent_alerts) == 0) {
  cat("> **No NWS alerts** recorded for", params$city, "area during the selected period.\n")
} else {
  disp <- recent_alerts %>% select(any_of(c("event","severity","urgency","sent"))) %>% head(25)
  if ("sent" %in% names(disp))
    disp$sent <- tryCatch(format(as.POSIXct(disp$sent, tz="UTC"), "%Y-%m-%d %H:%M"), error=function(e) disp$sent)
  kable(disp, booktabs=TRUE, linesep="") %>%
    kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE)
}
```

\newpage

# Current Road Conditions — Staff Access

```{r traffic-section, results='asis'}
if (nrow(traffic_df) == 0) {
  cat("> **No traffic incidents** currently recorded for", params$city, "county.\n")
} else {
  disp_t <- traffic_df %>%
    select(any_of(c("road","type","severity","is_full_closure","description"))) %>% head(20)
  if ("is_full_closure" %in% names(disp_t))
    disp_t$is_full_closure <- ifelse(disp_t$is_full_closure==TRUE, "YES", "no")
  if ("description" %in% names(disp_t))
    disp_t$description <- substr(disp_t$description, 1, 60)
  kable(disp_t, booktabs=TRUE, linesep="") %>%
    kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE)
}
```

**Impact on staff access:** `r if (n_closures >= 2) "CRITICAL — multiple roads closed. Staff must identify alternate routes before reporting." else if (n_closures == 1) "CAUTION — one road closure. Confirm alternate access before travel." else "No full closures detected. Normal staff commute expected."`

\newpage

# FCC Emergency Obligations

Broadcast stations have regulatory obligations during declared emergencies:

```{r fcc-table, results='asis'}
fcc_df <- data.frame(
  Obligation = c(
    "Emergency Alert System (EAS)","IPAWS/FEMA Integration",
    "Transmitter Operation","Staffing During Declared Emergency",
    "Damage Reporting","Public File Maintenance"
  ),
  Requirement = c(
    "Must relay Presidential and Required Weekly Test alerts. Monitor CAP/IPAWS feed continuously.",
    "FPREN beacon-ipaws-fetcher must remain operational; monitor for FL-specific CAP messages.",
    "Maintain authorized power; document any reduction due to emergency conditions.",
    "No minimum staffing requirement, but must maintain EAS capability from any location.",
    "Notify FCC within 24 hours if transmitter is silent >10 minutes due to emergency.",
    "Log all emergency alerts aired; retain for 2 years."
  ),
  `Action Item` = rep("[ ]", 6),
  stringsAsFactors=FALSE
)
kable(fcc_df, booktabs=TRUE, linesep="", col.names=c("FCC Obligation","Requirement","Done")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="4cm") %>%
  column_spec(2, width="8.5cm") %>%
  column_spec(3, width="1cm")
```

\newpage

# Recovery Timeline

```{r recovery-timeline, results='asis'}
timeline <- data.frame(
  Phase  = c(rep("Immediate (0-4 h)", 4), rep("Short-term (4-24 h)", 4),
             rep("Medium-term (1-7 d)", 3), rep("Long-term (7-30 d)", 2)),
  Action = c(
    "Activate staff notification tree; confirm head count",
    "Engineer assesses transmitter, antenna, generator status",
    "Enable automated emergency playlist if studio is unmanned",
    "Verify FPREN Icecast all 9 zone mounts streaming on port 8000",
    "Restore primary studio or activate alternate broadcast site",
    "Restore MongoDB from backup; restart all beacon-* services",
    "Confirm beacon-ipaws-fetcher delivering FL IPAWS alerts",
    "File FCC notification if transmitter was silent >10 min",
    "Replace or repair damaged equipment via UF procurement",
    "Full system test -- TTS generation across all 9 zones",
    "Resume normal programming; document incident",
    "Debrief staff; update this BCP with lessons learned",
    "Submit incident report to UF IT and FCC if required"
  ),
  Owner  = c("Manager","Engineer","Admin","Admin",
             "Engineer","IT Admin","IT Admin","Manager",
             "UF IT","Engineer","Manager","All","Manager"),
  Done   = rep("[ ]", 13),
  stringsAsFactors=FALSE
)
kable(timeline, booktabs=TRUE, linesep="", col.names=c("Phase","Action","Owner","Done")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, width="3.2cm", bold=TRUE, color=FPREN_BLUE) %>%
  column_spec(2, width="8cm") %>%
  column_spec(3, width="2.2cm") %>%
  column_spec(4, width="0.8cm")
```

\newpage

# Emergency Contacts

```{r contacts, results='asis'}
contacts <- data.frame(
  Role = c(
    "FPREN Administrator","UF IT Help Desk","UF Emergency Management",
    "FCC Operations Center","NWS Jacksonville (FL alerts)",
    "National Hurricane Center","UF Facilities Services",
    paste0(params$city, " County Emergency Mgmt"),
    "FL Division of Emergency Mgmt"
  ),
  Contact = c(
    "Lawrence Bornace -- lawrence.bornace@ufl.edu",
    "(352) 392-4357 -- helpdesk@ufl.edu",
    "(352) 392-1111 -- ufl.edu/emergency",
    "1-888-225-5322 (24/7 EAS emergency line)",
    "(904) 741-4311 -- weather.gov/jax",
    "(305) 229-4470 -- nhc.noaa.gov",
    "(352) 392-7793 -- facilities.ufl.edu",
    "(352) 264-6500",
    "(850) 413-9969 -- floridadisaster.org"
  ),
  stringsAsFactors=FALSE
)
kable(contacts, col.names=c("Role / Organization","Contact"), booktabs=TRUE, linesep="") %>%
  kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, color=FPREN_BLUE, width="6cm") %>%
  column_spec(2, width="9cm")
```

\vspace{16pt}
\begin{center}
\textcolor{fprenblue}{\rule{\linewidth}{1pt}}\\
\vspace{4pt}
{\small\textit{Generated by FPREN Automated Reporting -- `r format(Sys.time(), "%Y-%m-%d %H:%M ET")`}}\\
{\small\textit{Facility: `r params$asset_name` | User: `r params$username`}}\\
{\small Florida Public Radio Emergency Network --- University of Florida}
\end{center}
