---
title: "Business Continuity Plan — Campus Police Force"
subtitle: "`r params$asset_name`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
geometry: margin=1in
fontsize: 11pt
params:
  username: "user"
  asset_name: "University Police Department"
  address: "123 Main St, Gainesville, FL 32601"
  lat: 29.65
  lon: -82.33
  zip: "32601"
  city: "Gainesville"
  nearest_airport_icao: "KGNV"
  nearest_airport_name: "Gainesville Regional Airport"
  asset_type: "Office"
  notes: ""
  mongo_uri: "mongodb://localhost:27017/"
  days_back: 30
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE,
                      fig.align="center", out.width="90%")
suppressPackageStartupMessages({
  library(mongolite); library(dplyr); library(ggplot2)
  library(knitr); library(kableExtra); library(lubridate)
})
FPREN_BLUE  <- "#003087"
POLICE_NAVY <- "#1c2b6e"
start_date  <- Sys.time() - days(params$days_back)
mongo_uri   <- params$mongo_uri
safe_mongo  <- function(collection, db="weather_rss") {
  tryCatch(mongo(collection=collection, db=db, url=mongo_uri), error=function(e) NULL)
}
```

\definecolor{fprenblue}{HTML}{003087}
\definecolor{policenavy}{HTML}{1c2b6e}

\begin{center}
\textcolor{policenavy}{\rule{\linewidth}{2pt}}
\vspace{4pt}
{\Large\textbf{\textcolor{policenavy}{FPREN --- Florida Public Radio Emergency Network}}}\\
{\large\textbf{Campus Police Force Business Continuity Plan}}\\
{\normalsize\textit{`r params$asset_name` --- `r params$city`}}\\
\vspace{4pt}
\textcolor{policenavy}{\rule{\linewidth}{1pt}}
\end{center}

\vspace{6pt}

```{r cover-table, results='asis'}
cover <- data.frame(
  Field = c("Department / Unit","Address","Coordinates",
            "Jurisdiction City","Nearest Airport","Prepared By",
            "Classification","Report Generated","Analysis Period"),
  Value = c(params$asset_name, params$address,
            paste0(params$lat, " N, ", abs(params$lon), " W"),
            params$city,
            paste0(params$nearest_airport_icao, " -- ", params$nearest_airport_name),
            params$username,
            "LAW ENFORCEMENT SENSITIVE",
            format(Sys.time(), "%Y-%m-%d %H:%M ET"),
            paste0(params$days_back, " days")),
  stringsAsFactors=FALSE
)
kable(cover, col.names=NULL, booktabs=TRUE, linesep="") %>%
  kable_styling(latex_options="hold_position", full_width=FALSE) %>%
  column_spec(1, bold=TRUE, color=POLICE_NAVY, width="6cm") %>%
  column_spec(2, width="9cm")
```

> **LAW ENFORCEMENT SENSITIVE** -- Distribution limited to authorized personnel.

\newpage

# Executive Summary

```{r exec-summary}
alerts_col    <- safe_mongo("nws_alerts")
recent_alerts <- tryCatch({
  if (is.null(alerts_col)) stop()
  q <- sprintf('{"$or":[{"area_desc":{"$regex":"%s","$options":"i"}},{"counties":{"$regex":"%s","$options":"i"}}]}',
               params$city, params$city)
  r <- alerts_col$find(q, fields='{"event":1,"severity":1,"urgency":1,"sent":1,"expires":1,"_id":0}')
  alerts_col$disconnect(); r
}, error=function(e) { tryCatch(alerts_col$disconnect(), error=function(e2) NULL); data.frame() })

n_alerts   <- nrow(recent_alerts)
n_extreme  <- if (n_alerts > 0 && "severity" %in% names(recent_alerts))
                sum(tolower(recent_alerts$severity) %in% c("extreme","severe"), na.rm=TRUE) else 0
alert_risk <- if (n_extreme >= 3) "HIGH" else if (n_extreme >= 1 || n_alerts >= 5) "MODERATE" else "LOW"

wx_col  <- safe_mongo("weather_history")
wx_hist <- tryCatch({
  if (is.null(wx_col)) stop()
  r <- wx_col$find(
    sprintf('{"icao":"%s","timestamp":{"$gte":"%s"}}', params$nearest_airport_icao,
            format(start_date, "%Y-%m-%dT%H:%M:%SZ")),
    fields='{"temp_f":1,"wind_speed":1,"flight_cat":1,"_id":0}')
  wx_col$disconnect(); r
}, error=function(e) { tryCatch(wx_col$disconnect(), error=function(e2) NULL); data.frame() })
max_wind <- if (nrow(wx_hist) > 0 && "wind_speed" %in% names(wx_hist))
              max(wx_hist$wind_speed, na.rm=TRUE) else NA_real_
n_ifr    <- if (nrow(wx_hist) > 0 && "flight_cat" %in% names(wx_hist))
              sum(wx_hist$flight_cat %in% c("IFR","LIFR"), na.rm=TRUE) else 0
wx_risk  <- if (!is.na(max_wind) && (max_wind > 40 || n_ifr > 10)) "HIGH" else
            if (!is.na(max_wind) && (max_wind > 25 || n_ifr > 3)) "MODERATE" else "LOW"

traffic_col <- safe_mongo("fl_traffic")
traffic_df  <- tryCatch({
  if (is.null(traffic_col)) stop()
  r <- traffic_col$find(
    sprintf('{"county":{"$regex":"%s","$options":"i"}}', params$city),
    fields='{"type":1,"severity":1,"is_full_closure":1,"road":1,"description":1,"_id":0}')
  traffic_col$disconnect(); r
}, error=function(e) { tryCatch(traffic_col$disconnect(), error=function(e2) NULL); data.frame() })
n_closures   <- if (nrow(traffic_df) > 0 && "is_full_closure" %in% names(traffic_df))
                  sum(traffic_df$is_full_closure==TRUE, na.rm=TRUE) else 0
traffic_risk <- if (n_closures >= 2) "HIGH" else
                if (n_closures >= 1 || nrow(traffic_df) > 5) "MODERATE" else "LOW"

evac_col <- safe_mongo("fl_evacuation_zones")
evac_zones_df <- tryCatch({
  if (is.null(evac_col)) stop()
  r <- evac_col$find(
    sprintf('{"county":{"$regex":"^%s$","$options":"i"}}', params$city),
    fields='{"zone":1,"zone_order":1,"description":1,"_id":0}', sort='{"zone_order":1}')
  evac_col$disconnect(); r
}, error=function(e) { tryCatch(evac_col$disconnect(), error=function(e2) NULL); data.frame() })
highest_zone <- if (nrow(evac_zones_df) > 0) evac_zones_df$zone[1] else NA
evac_risk    <- if (!is.na(highest_zone) && highest_zone == "A") "HIGH" else
                if (!is.na(highest_zone) && highest_zone %in% c("B","C")) "MODERATE" else "LOW"

census_col <- safe_mongo("fl_census")
census_rec <- tryCatch({
  if (is.null(census_col)) stop()
  r <- census_col$find(
    sprintf('{"county":{"$regex":"^%s$","$options":"i"}}', params$city),
    sort='{"year":-1}', limit=1,
    fields='{"population_total":1,"pct_65plus":1,"pct_disability":1,"pct_limited_english":1,"_id":0}')
  census_col$disconnect()
  if (nrow(r)==0) NULL else r[1,]
}, error=function(e) { tryCatch(census_col$disconnect(), error=function(e2) NULL); NULL })

overall_risks <- c(alert_risk, wx_risk, traffic_risk, evac_risk)
overall_risk  <- if (any(overall_risks=="HIGH")) "HIGH" else
                 if (any(overall_risks=="MODERATE")) "MODERATE" else "LOW"
```

This plan covers **`r params$asset_name`** in **`r params$city`**. It integrates live weather alerts, road conditions, evacuation zone status, and population vulnerability data to support campus police operations during natural disasters and large-scale emergencies.

```{r risk-table, results='asis'}
risk_df <- data.frame(
  Category = c("Weather / Severe Events","NWS Alert Activity",
               "Campus Road Access","Evacuation Zone Status","Overall Threat Level"),
  Level    = c(wx_risk, alert_risk, traffic_risk, evac_risk, overall_risk),
  Detail   = c(
    if (!is.na(max_wind)) paste0("Max wind: ", round(max_wind,1), " mph; IFR hours: ", n_ifr)
    else "No weather history",
    paste0(n_alerts, " alerts; ", n_extreme, " Extreme/Severe"),
    paste0(n_closures, " full road closures; ", nrow(traffic_df), " incidents"),
    if (!is.na(highest_zone)) paste0("Highest zone: ", highest_zone)
    else "No evacuation zone data",
    paste0(params$days_back, "-day assessment")
  ),
  stringsAsFactors=FALSE
)
kable(risk_df, col.names=c("Risk Category","Level","Detail"), booktabs=TRUE, linesep="") %>%
  kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
  column_spec(2, bold=TRUE,
    color=ifelse(risk_df$Level=="HIGH","red",ifelse(risk_df$Level=="MODERATE","orange","#2e7d32")))
```

\newpage

# Personnel Deployment Plan

## Staffing Levels by Alert Phase

```{r staffing-table, results='asis'}
staff_df <- data.frame(
  Phase = c(
    "Normal Operations","Watch Issued","Warning Issued",
    "Mandatory Evacuation Ordered","Active Event / Shelter-in-Place",
    "Post-Event Recovery"
  ),
  Staffing = c(
    "Normal shift rotation",
    "Recall one extra shift; brief all officers",
    "Full recall; no days off; 12-hour shifts",
    "All personnel on duty; assist with evacuation traffic",
    "All personnel on duty; 12-hour shifts; mandatory rest rotation",
    "Staggered shifts; damage patrol; re-entry control"
  ),
  `Command Center` = c("Normal","Department HQ","Department HQ / EOC liaison",
                       "Campus EOC activated","Campus EOC full activation","EOC active"),
  `FPREN Integration` = c("Monitor alerts","Monitor FPREN Zone broadcasts",
                           "Relay FPREN warnings to campus dispatch",
                           "Broadcast evac orders via PA + FPREN",
                           "Monitor FPREN for all-clear / shelter updates",
                           "FPREN re-entry zone broadcasts"),
  stringsAsFactors=FALSE, check.names=FALSE
)
kable(staff_df, booktabs=TRUE, linesep="",
      col.names=c("Emergency Phase","Staffing Level","Command Posture","FPREN Integration")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="3.5cm") %>%
  column_spec(2, width="4cm") %>%
  column_spec(3, width="3cm") %>%
  column_spec(4, width="4.5cm")
```

## Campus Sector Assignments (Emergency Deployment)

```{r sectors, results='asis'}
sectors_df <- data.frame(
  Sector = c(
    "Sector A — Central Campus","Sector B — Residence Halls",
    "Sector C — Medical / Research","Sector D — Athletic / Parking",
    "Sector E — Perimeter / Roads","Command Post"
  ),
  Priority = c("High","Critical","Critical","Moderate","High","Fixed"),
  Responsibilities = c(
    "Main entry points; administrative buildings; library",
    "Student evacuation assistance; ADA resident assistance; shelter-in-place monitoring",
    "Hospital/clinic coordination; lab chemical hazard monitoring; generator security",
    "Crowd control at storm shelters; vehicle pre-positioning",
    "Traffic control at campus gates; evacuation route management; road closure enforcement",
    "ICS command; dispatch coordination; EOC liaison"
  ),
  `Officers Assigned` = c("2","3","2","1","2","1"),
  stringsAsFactors=FALSE, check.names=FALSE
)
kable(sectors_df, booktabs=TRUE, linesep="",
      col.names=c("Campus Sector","Priority","Responsibilities","Min. Officers")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="4cm") %>%
  column_spec(2, width="1.8cm") %>%
  column_spec(3, width="8cm") %>%
  column_spec(4, width="1.5cm")
```

\newpage

# Evacuation Assistance — Vulnerable Populations

```{r vulnerable-pop, results='asis'}
vp_df <- data.frame(
  Group = c(
    "Mobility-impaired students/residents",
    "International students (Limited English)",
    "Graduate student researchers (in labs)",
    "Hospital / clinic patients",
    "Elderly visitors / conference attendees"
  ),
  `Identification Method` = c(
    "Disability Services Office roster; ADA accommodations list",
    "International Student Center database; flags in dispatch system",
    "Lab access logs; Department contact tree",
    "Health Services / Shands coordination",
    "Conference Services notification"
  ),
  `Evacuation Action` = c(
    "Two-officer teams; marked 'Areas of Refuge' on each floor; contact Facilities lift units",
    "Bilingual officer assigned; coordinate with International Student Center",
    "Floor warden system; hazmat awareness before evacuation",
    "Coordinate with Health Services staff; do not move critical patients without clinical guidance",
    "Campus escort to designated shelter; contact event organizer"
  ),
  stringsAsFactors=FALSE, check.names=FALSE
)
kable(vp_df, booktabs=TRUE, linesep="",
      col.names=c("Vulnerable Group","ID Method","Evacuation Protocol")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="3.5cm") %>%
  column_spec(2, width="4.5cm") %>%
  column_spec(3, width="7cm")
```

```{r census-vuln, results='asis'}
if (!is.null(census_rec)) {
  safe_num <- function(x) tryCatch(as.numeric(x), error=function(e) 0)
  cat(sprintf(
    "\n**%s County context:** %.1f%% of county population has a disability; %.1f%% are 65+; %.1f%% have limited English proficiency. Campus ADA and LEP populations mirror these county demographics and require proactive outreach during emergency events.\n\n",
    params$city,
    safe_num(census_rec$pct_disability),
    safe_num(census_rec$pct_65plus),
    safe_num(census_rec$pct_limited_english)
  ))
}
```

\newpage

# Current Threat Conditions

## Active NWS Alerts

```{r alerts-section, results='asis'}
if (nrow(recent_alerts) == 0) {
  cat("> **No active NWS alerts** for", params$city, "area.\n")
} else {
  disp <- recent_alerts %>% select(any_of(c("event","severity","urgency","sent"))) %>% head(20)
  if ("sent" %in% names(disp))
    disp$sent <- tryCatch(format(as.POSIXct(disp$sent, tz="UTC"), "%Y-%m-%d %H:%M"), error=function(e) disp$sent)
  kable(disp, booktabs=TRUE, linesep="") %>%
    kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE)
}
```

## Road Conditions — Campus Access Routes

```{r traffic-section, results='asis'}
if (nrow(traffic_df) == 0) {
  cat("> **No FL511 traffic incidents** recorded for", params$city, "county.\n")
} else {
  disp_t <- traffic_df %>%
    select(any_of(c("road","type","severity","is_full_closure","description"))) %>% head(20)
  if ("is_full_closure" %in% names(disp_t))
    disp_t$is_full_closure <- ifelse(disp_t$is_full_closure==TRUE, "YES","no")
  if ("description" %in% names(disp_t))
    disp_t$description <- substr(disp_t$description, 1, 60)
  kable(disp_t, booktabs=TRUE, linesep="") %>%
    kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE)
}
```

`r if (n_closures > 0) paste0("**ROAD CLOSURE ALERT:** ", n_closures, " full road closure(s) in county. Review alternate patrol routes and campus gate access points.")`

\newpage

# Inter-Agency Coordination

## Campus Emergency Response Partners

```{r partners, results='asis'}
partners_df <- data.frame(
  Agency = c(
    "Campus Police Command","University Emergency Management",
    paste0(params$city, " County Sheriff"),
    paste0(params$city, " City Police"),
    paste0(params$city, " Fire Rescue"),
    "FL Highway Patrol (FHP)",
    "FL National Guard","Gainesville Fire Rescue",
    "FPREN (Mass Notification)"
  ),
  Role = c(
    "Primary incident command on campus",
    "EOC activation; resource coordination; NIMS compliance",
    "Mutual aid; perimeter security; major crime response",
    "City traffic control; off-campus crime response",
    "Fire / EMS response; HAZMAT; rescue operations",
    "Major roadway traffic management; evacuation routes",
    "State asset requests; search and rescue support",
    "EMS and fire response in city limits",
    "FPREN broadcasts weather alerts, shelter locations, re-entry"
  ),
  `Liaison / Radio` = c(
    "UPD Dispatch: Channel 1","UEM: (352) 392-1111",
    "(352) 367-4000 -- Channel 3",
    "(352) 955-1818 -- Channel 4",
    "(352) 334-5058 -- Channel 5",
    "*FHP: (850) 617-3100",
    "JFHQ: (904) 823-0550",
    "Station 1: (352) 334-5058",
    "FPREN Admin: (352) 392-xxxx"
  ),
  `MOU on File` = rep("[ ]", 9),
  stringsAsFactors=FALSE, check.names=FALSE
)
kable(partners_df, booktabs=TRUE, linesep="",
      col.names=c("Agency","Role During Emergency","Contact / Channel","MOU")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="3.5cm") %>%
  column_spec(2, width="5.5cm") %>%
  column_spec(3, width="3.5cm") %>%
  column_spec(4, width="0.8cm")
```

## FPREN Broadcast Coordination

Campus Police monitors the following FPREN Icecast zone mounts during emergencies:

- **Primary zone:** `/gainesville` — Alachua County area alerts (port 8000)
- **Secondary:** `/all_florida` — statewide IPAWS alerts
- **Action:** If FPREN broadcasts a tornado warning or hurricane warning, activate campus-wide PA and UF Alert immediately.

\newpage

# Vehicle Pre-Positioning & Equipment

```{r equipment-checklist, results='asis'}
equip_df <- data.frame(
  Item = c(
    "Patrol vehicles (fuel > 3/4 tank)","Emergency generators (fuel + test run)",
    "Traffic control equipment (cones, signs, lights)",
    "Prisoner transport / evacuation transport vehicle",
    "Portable radios (charged + extra batteries)",
    "Megaphones / PA units","First aid / trauma kits",
    "Rain gear and PPE for all officers",
    "Emergency contact flip-book (physical copy)",
    "Incident Command vests (ICS roles)"
  ),
  `Pre-Event Check` = rep("[ ]", 10),
  `Post-Event Check` = rep("[ ]", 10),
  `Notes` = c(
    "Min. 3/4 tank before storm landfall",
    "Generator: HQ, Records, and Dispatch must be on backup",
    "Pre-stage at campus gates and main intersections",
    "Coordinate with Student Affairs for student transport",
    "All portable radios on Channel 1 for event; Channel 9 mutual aid",
    "One per sector; test before deployment",
    "Check expiration dates; restock if needed",
    "Issue to all officers before storm landfall",
    "Update list 48h before any forecasted event",
    "ICS vests for: IC, Operations, Logistics, Liaison, Safety"
  ),
  stringsAsFactors=FALSE
)
kable(equip_df, booktabs=TRUE, linesep="",
      col.names=c("Equipment Item","Pre-Event","Post-Event","Notes")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, width="5cm") %>%
  column_spec(2, width="1.8cm") %>%
  column_spec(3, width="1.8cm") %>%
  column_spec(4, width="5.5cm")
```

\newpage

# Recovery Timeline

```{r recovery-timeline, results='asis'}
timeline <- data.frame(
  Phase  = c(rep("Immediate (0-4 h)", 4), rep("Short-term (4-24 h)", 4),
             rep("Medium-term (1-7 d)", 3), rep("Long-term (7-30 d)", 2)),
  Action = c(
    "Officer accountability — confirm all personnel safe",
    "Damage patrol of all campus buildings and roads",
    "Establish and enforce perimeter / access control",
    "Coordinate with University Emergency Management at EOC",
    "Staged re-entry: essential staff first, then students",
    "Traffic control at campus gates for re-entry",
    "Secure damaged buildings; coordinate with Facilities",
    "Coordinate with County Sheriff on mutual aid release",
    "Return to normal patrol rotation as campus recovers",
    "Debrief all officers; document incident timeline",
    "Review and update this BCP; submit AAR to UEM",
    "Identify equipment/training gaps from incident",
    "Update mutual aid agreements and contact lists"
  ),
  Owner  = c("Chief","All Officers","Shift Supervisors","Chief",
             "Shift Supervisors","Traffic Unit","Facilities Liaison","Chief",
             "Shift Supervisors","All Officers","Chief","Training Unit","Chief"),
  Done   = rep("[ ]", 13),
  stringsAsFactors=FALSE
)
kable(timeline, booktabs=TRUE, linesep="", col.names=c("Phase","Action","Owner","Done")) %>%
  kable_styling(latex_options=c("hold_position","striped","scale_down"), full_width=FALSE) %>%
  column_spec(1, width="3.2cm", bold=TRUE, color=POLICE_NAVY) %>%
  column_spec(2, width="8cm") %>%
  column_spec(3, width="2.8cm") %>%
  column_spec(4, width="0.8cm")
```

\newpage

# Emergency Contacts

```{r contacts, results='asis'}
contacts <- data.frame(
  Role = c(
    "University Police Department (Dispatch)","University Emergency Management",
    "UF President / Provost Office",
    paste0(params$city, " County Sheriff's Office"),
    paste0(params$city, " City Police Department"),
    paste0(params$city, " Fire Rescue"),
    "FL Highway Patrol (FHP) Troop C",
    "FL Division of Emergency Management",
    "National Weather Service Jacksonville",
    "FPREN Administrator"
  ),
  Contact = c(
    "(352) 392-1111 (non-emergency) / 911",
    "(352) 392-1111 -- ufl.edu/emergency",
    "(352) 392-1311",
    "(352) 367-4000",
    "(352) 955-1818",
    "(352) 334-5058",
    "(850) 617-3100",
    "(850) 413-9969 -- floridadisaster.org",
    "(904) 741-4311 -- weather.gov/jax",
    "lawrence.bornace@ufl.edu"
  ),
  stringsAsFactors=FALSE
)
kable(contacts, col.names=c("Role / Agency","Contact"),
      booktabs=TRUE, linesep="") %>%
  kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
  column_spec(1, bold=TRUE, color=POLICE_NAVY, width="6.5cm") %>%
  column_spec(2, width="8.5cm")
```

\vspace{16pt}
\begin{center}
\textcolor{policenavy}{\rule{\linewidth}{1pt}}\\
\vspace{4pt}
{\small\textit{Generated by FPREN Automated Reporting -- `r format(Sys.time(), "%Y-%m-%d %H:%M ET")`}}\\
{\small\textit{Department: `r params$asset_name` | Prepared by: `r params$username`}}\\
{\small\textbf{LAW ENFORCEMENT SENSITIVE} --- Florida Public Radio Emergency Network}
\end{center}
