---
title: "Business Continuity Plan"
subtitle: "`r params$asset_name`"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
geometry: margin=1in
fontsize: 11pt
params:
  username: "user"
  asset_name: "Asset Name"
  address: "123 Main St, Gainesville, FL 32601"
  lat: 29.65
  lon: -82.33
  zip: "32601"
  city: "Gainesville"
  nearest_airport_icao: "KGNV"
  nearest_airport_name: "Gainesville Regional Airport"
  asset_type: "Facility"
  notes: ""
  mongo_uri: "mongodb://localhost:27017/"
  days_back: 30
  other_assets_json: "[]"
  profession: "General"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", out.width = "90%")
suppressPackageStartupMessages({
  library(mongolite)
  library(dplyr)
  library(ggplot2)
  library(knitr)
  library(kableExtra)
  library(lubridate)
})

FPREN_BLUE <- "#003087"
start_date <- Sys.time() - days(params$days_back)
mongo_uri  <- params$mongo_uri

safe_mongo <- function(collection, db = "weather_rss") {
  tryCatch(
    mongo(collection = collection, db = db, url = mongo_uri),
    error = function(e) NULL
  )
}
```

\definecolor{fprenblue}{HTML}{003087}

\begin{center}
\textcolor{fprenblue}{\rule{\linewidth}{2pt}}
\vspace{4pt}
{\Large\textbf{\textcolor{fprenblue}{FPREN --- Florida Public Radio Emergency Network}}}\\
{\large Business Continuity Plan}\\
\vspace{4pt}
\textcolor{fprenblue}{\rule{\linewidth}{1pt}}
\end{center}

\vspace{6pt}

```{r cover-table, results='asis'}
cover <- data.frame(
  Field = c("Asset / Property", "Asset Type", "Address", "Coordinates",
            "Nearest City", "Nearest Airport", "Owner / User",
            "Report Generated", "Days Covered"),
  Value = c(params$asset_name, params$asset_type, params$address,
            paste0(params$lat, " N, ", abs(params$lon), " W"),
            params$city,
            paste0(params$nearest_airport_icao, " -- ", params$nearest_airport_name),
            params$username,
            format(Sys.time(), "%Y-%m-%d %H:%M ET"),
            paste0(params$days_back, " days")),
  stringsAsFactors = FALSE
)
kable(cover, col.names = NULL, booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("hold_position"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, color = FPREN_BLUE, width = "6cm") %>%
  column_spec(2, width = "9cm")
```

\vspace{8pt}

> **Confidential** -- This Business Continuity Plan is for authorized FPREN personnel only.

\newpage

# Executive Summary

```{r exec-summary}
# --- Recent alerts for this city/county ---
alerts_col <- safe_mongo("nws_alerts")
recent_alerts <- tryCatch({
  if (is.null(alerts_col)) stop("no connection")
  q <- sprintf(
    '{"$or":[{"area_desc":{"$regex":"%s","$options":"i"}},{"counties":{"$regex":"%s","$options":"i"}}]}',
    params$city, params$city
  )
  r <- alerts_col$find(q,
    fields = '{"event":1,"severity":1,"urgency":1,"sent":1,"expires":1,"_id":0}')
  alerts_col$disconnect()
  r
}, error = function(e) {
  tryCatch(alerts_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

n_alerts  <- nrow(recent_alerts)
n_extreme <- if (n_alerts > 0 && "severity" %in% names(recent_alerts)) {
               sum(tolower(recent_alerts$severity) %in% c("extreme","severe"), na.rm = TRUE)
             } else 0
alert_risk <- if (n_extreme >= 3) "HIGH" else if (n_extreme >= 1 || n_alerts >= 5) "MODERATE" else "LOW"

# --- Weather history for nearest station ---
wx_col  <- safe_mongo("weather_history")
wx_hist <- tryCatch({
  if (is.null(wx_col)) stop("no connection")
  q <- sprintf('{"icao":"%s","timestamp":{"$gte":"%s"}}',
               params$nearest_airport_icao,
               format(start_date, "%Y-%m-%dT%H:%M:%SZ"))
  r <- wx_col$find(q,
    fields = '{"temp_f":1,"wind_speed":1,"flight_cat":1,"visibility":1,"_id":0}')
  wx_col$disconnect()
  r
}, error = function(e) {
  tryCatch(wx_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

n_wx     <- nrow(wx_hist)
n_ifr    <- if (n_wx > 0 && "flight_cat" %in% names(wx_hist))
              sum(wx_hist$flight_cat %in% c("IFR","LIFR"), na.rm = TRUE) else 0
max_wind <- if (n_wx > 0 && "wind_speed" %in% names(wx_hist))
              max(wx_hist$wind_speed, na.rm = TRUE) else NA_real_
wx_risk  <- if (!is.na(max_wind) && (max_wind > 40 || n_ifr > 10)) "HIGH" else
            if (!is.na(max_wind) && (max_wind > 25 || n_ifr > 3))  "MODERATE" else "LOW"

# --- Traffic ---
traffic_col <- safe_mongo("fl_traffic")
traffic_df  <- tryCatch({
  if (is.null(traffic_col)) stop("no connection")
  q <- sprintf('{"county":{"$regex":"%s","$options":"i"}}', params$city)
  r <- traffic_col$find(q,
    fields = '{"type":1,"severity":1,"is_full_closure":1,"road":1,"description":1,"_id":0}')
  traffic_col$disconnect()
  r
}, error = function(e) {
  tryCatch(traffic_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

n_closures   <- if (nrow(traffic_df) > 0 && "is_full_closure" %in% names(traffic_df))
                  sum(traffic_df$is_full_closure == TRUE, na.rm = TRUE) else 0
traffic_risk <- if (n_closures >= 2) "HIGH" else
                if (n_closures >= 1 || nrow(traffic_df) > 5) "MODERATE" else "LOW"

# --- Evacuation Zones ---
evac_zones_col <- safe_mongo("fl_evacuation_zones")
evac_zones_df  <- tryCatch({
  if (is.null(evac_zones_col)) stop("no connection")
  q <- sprintf('{"county":{"$regex":"^%s$","$options":"i"}}', params$city)
  r <- evac_zones_col$find(q,
    fields = '{"zone":1,"zone_order":1,"description":1,"has_coastal":1,"source":1,"_id":0}',
    sort = '{"zone_order":1}')
  evac_zones_col$disconnect()
  r
}, error = function(e) {
  tryCatch(evac_zones_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

# --- Evacuation Routes ---
evac_routes_col <- safe_mongo("fl_evacuation_routes")
evac_routes_df  <- tryCatch({
  if (is.null(evac_routes_col)) stop("no connection")
  q <- sprintf('{"county":{"$regex":"^%s$","$options":"i"}}', params$city)
  r <- evac_routes_col$find(q,
    fields = '{"name":1,"road":1,"direction":1,"from_location":1,"to_location":1,"route_type":1,"serves_zones":1,"_id":0}',
    sort = '{"route_type":1}')
  evac_routes_col$disconnect()
  r
}, error = function(e) {
  tryCatch(evac_routes_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

highest_zone  <- if (nrow(evac_zones_df) > 0) evac_zones_df$zone[1] else NA
n_evac_routes <- nrow(evac_routes_df)
evac_risk     <- if (!is.na(highest_zone) && highest_zone == "A") "HIGH" else
                 if (!is.na(highest_zone) && highest_zone %in% c("B","C")) "MODERATE" else "LOW"

# --- Check traffic on evacuation route roads ---
evac_route_roads <- if (nrow(evac_routes_df) > 0 && "road" %in% names(evac_routes_df))
                      paste(evac_routes_df$road, collapse="|") else ""
traffic_on_evac_routes <- if (nchar(evac_route_roads) > 0 && nrow(traffic_df) > 0 &&
                               "road" %in% names(traffic_df)) {
  traffic_df[grepl(evac_route_roads, traffic_df$road, ignore.case=TRUE), ]
} else data.frame()

overall_risks <- c(alert_risk, wx_risk, traffic_risk, evac_risk)
overall_risk  <- if (any(overall_risks == "HIGH")) "HIGH" else
                 if (any(overall_risks == "MODERATE")) "MODERATE" else "LOW"
```

This Business Continuity Plan covers **`r params$asset_name`** at `r params$address`.
Analysis period: `r params$days_back` days ending `r format(Sys.Date(), "%B %d, %Y")`.

```{r risk-table, results='asis'}
risk_df <- data.frame(
  Category = c("Weather / Aviation Risk", "NWS Alert Activity",
               "Traffic / Road Access", "Evacuation Zone Risk", "Overall Risk Level"),
  Level    = c(wx_risk, alert_risk, traffic_risk, evac_risk, overall_risk),
  Detail   = c(
    if (!is.na(max_wind)) paste0("Max wind: ", round(max_wind,1), " mph; IFR/LIFR hours: ", n_ifr)
    else "No weather history available",
    paste0(n_alerts, " alerts; ", n_extreme, " Extreme/Severe"),
    paste0(n_closures, " full closures; ", nrow(traffic_df), " total incidents"),
    if (!is.na(highest_zone))
      paste0("Highest zone: ", highest_zone, "; ", n_evac_routes, " designated evacuation routes")
    else "No evacuation zone data",
    paste0("Combined ", params$days_back, "-day assessment")
  ),
  stringsAsFactors = FALSE
)
kable(risk_df, col.names = c("Risk Category","Level","Detail"),
      booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("hold_position","striped"), full_width = FALSE) %>%
  column_spec(2, bold = TRUE,
    color = ifelse(risk_df$Level == "HIGH", "red",
             ifelse(risk_df$Level == "MODERATE", "orange", "#2e7d32")))
```

`r if (nchar(params$notes) > 0) paste0("**Notes:** ", params$notes)`

\newpage

# Asset Location Overview

```{r asset-location, results='asis'}
loc_df <- data.frame(
  Field = c("Full Address","Latitude","Longitude","ZIP Code",
            "Nearest Major City","Nearest Airport (ICAO)","Airport Name"),
  Value = c(params$address,
            paste0(params$lat, " N"),
            paste0(abs(params$lon), " W"),
            params$zip, params$city,
            params$nearest_airport_icao,
            params$nearest_airport_name),
  stringsAsFactors = FALSE
)
kable(loc_df, col.names = NULL, booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = "hold_position", full_width = FALSE) %>%
  column_spec(1, bold = TRUE, color = FPREN_BLUE, width = "6cm") %>%
  column_spec(2, width = "9cm")
```

**GPS Coordinates:** `r params$lat`, `r params$lon`

\newpage

# Weather Risk Assessment

Historical data from **`r params$nearest_airport_icao`** (`r params$nearest_airport_name`),
last `r params$days_back` days.

```{r weather-analysis, results='asis', fig.height=3.5}
if (nrow(wx_hist) == 0) {
  cat("> **No weather history available** for this station during the selected period.\n")
} else {
  avg_temp  <- round(mean(wx_hist$temp_f,   na.rm = TRUE), 1)
  min_temp  <- round(min(wx_hist$temp_f,    na.rm = TRUE), 1)
  max_temp  <- round(max(wx_hist$temp_f,    na.rm = TRUE), 1)
  avg_wind  <- if ("wind_speed" %in% names(wx_hist))
                 round(mean(wx_hist$wind_speed, na.rm = TRUE), 1) else NA
  max_wind2 <- if ("wind_speed" %in% names(wx_hist))
                 round(max(wx_hist$wind_speed,  na.rm = TRUE), 1) else NA
  n_vfr  <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat == "VFR",  na.rm=TRUE) else 0
  n_mvfr <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat == "MVFR", na.rm=TRUE) else 0
  n_ifr2 <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat == "IFR",  na.rm=TRUE) else 0
  n_lifr <- if ("flight_cat" %in% names(wx_hist)) sum(wx_hist$flight_cat == "LIFR", na.rm=TRUE) else 0

  wx_stats <- data.frame(
    Metric = c("Avg Temp","Min Temp","Max Temp",
               "Avg Wind","Max Wind",
               "VFR Hours","MVFR Hours","IFR Hours","LIFR Hours"),
    Value  = c(paste0(avg_temp," F"), paste0(min_temp," F"), paste0(max_temp," F"),
               if (!is.na(avg_wind)) paste0(avg_wind," mph") else "N/A",
               if (!is.na(max_wind2)) paste0(max_wind2," mph") else "N/A",
               n_vfr, n_mvfr, n_ifr2, n_lifr),
    stringsAsFactors = FALSE
  )
  print(
    kable(wx_stats, col.names = c("Metric","Value"), booktabs = TRUE, linesep = "") %>%
      kable_styling(latex_options = c("hold_position","striped"), full_width = FALSE) %>%
      column_spec(1, width = "7cm") %>%
      column_spec(2, width = "4cm")
  )

  if ("flight_cat" %in% names(wx_hist) && nrow(wx_hist) > 0) {
    cat_counts <- wx_hist %>%
      filter(!is.na(flight_cat)) %>%
      group_by(flight_cat) %>%
      summarise(n = n(), .groups = "drop") %>%
      mutate(flight_cat = factor(flight_cat, levels = c("VFR","MVFR","IFR","LIFR")))
    cat_colors <- c(VFR="#0077aa", MVFR="#f0c030", IFR="#e07020", LIFR="#cc2222")
    p <- ggplot(cat_counts, aes(x = flight_cat, y = n, fill = flight_cat)) +
      geom_col(width = 0.6) +
      scale_fill_manual(values = cat_colors, guide = "none") +
      labs(title = paste0("Flight Category Distribution -- ", params$nearest_airport_icao),
           x = "Category", y = "Hours") +
      theme_minimal(base_size = 11) +
      theme(plot.title = element_text(color = FPREN_BLUE, face = "bold"))
    print(p)
  }
}
```

\newpage

# Recent Alert History

NWS alerts for **`r params$city`** area, last `r params$days_back` days.

```{r alerts-section, results='asis'}
if (nrow(recent_alerts) == 0) {
  cat("> **No NWS alerts** recorded for this area during the selected period.\n")
} else {
  disp <- recent_alerts %>%
    select(any_of(c("event","severity","urgency","sent"))) %>%
    head(25)
  if ("sent" %in% names(disp))
    disp$sent <- tryCatch(
      format(as.POSIXct(disp$sent, tz = "UTC"), "%Y-%m-%d %H:%M"),
      error = function(e) disp$sent)
  kable(disp, booktabs = TRUE, linesep = "") %>%
    kable_styling(latex_options = c("hold_position","striped","scale_down"),
                  full_width = FALSE)
}
```

\newpage

# Traffic & Evacuation Analysis

## Hurricane Evacuation Zones — `r params$city` County

```{r evac-zones-section, results='asis'}
if (nrow(evac_zones_df) == 0) {
  cat("> **No evacuation zone data** found for this county.\n")
} else {
  zone_disp <- evac_zones_df %>%
    select(any_of(c("zone","description","has_coastal","source")))
  names(zone_disp)[names(zone_disp) == "zone"] <- "Zone"
  names(zone_disp)[names(zone_disp) == "description"] <- "Description"
  names(zone_disp)[names(zone_disp) == "has_coastal"] <- "Coastal Exposure"
  names(zone_disp)[names(zone_disp) == "source"] <- "Source"
  if ("Coastal Exposure" %in% names(zone_disp))
    zone_disp[["Coastal Exposure"]] <- ifelse(zone_disp[["Coastal Exposure"]] == TRUE, "Yes", "No")
  kable(zone_disp, booktabs = TRUE, linesep = "", row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position","striped"),
                  full_width = FALSE) %>%
    column_spec(1, bold = TRUE, color = FPREN_BLUE, width = "1.2cm") %>%
    column_spec(2, width = "10cm")
}
```

```{r evac-zone-summary, results='asis'}
if (!is.na(highest_zone)) {
  zone_msg <- if (highest_zone == "A") {
    "Zone A is mandatory evacuation territory -- residents must evacuate for any hurricane."
  } else if (highest_zone == "B") {
    "Zone B requires evacuation for Category 1+ hurricanes."
  } else if (highest_zone == "C") {
    "Zone C requires evacuation for Category 2+ hurricanes."
  } else {
    paste0("Zone ", highest_zone, " requires evacuation for major hurricanes.")
  }
  cat(paste0("**This asset's county has evacuation zones up to Zone ", highest_zone, ".** ", zone_msg, "\n"))
}
```

## Designated Evacuation Routes

```{r evac-routes-section, results='asis'}
if (nrow(evac_routes_df) == 0) {
  cat("> **No designated evacuation routes** recorded for this county.\n")
} else {
  route_disp <- evac_routes_df %>%
    select(any_of(c("name","road","direction","from_location","to_location","route_type","serves_zones")))
  if ("serves_zones" %in% names(route_disp))
    route_disp$serves_zones <- sapply(route_disp$serves_zones, function(z)
      if (is.list(z)) paste(unlist(z), collapse=", ") else paste(z, collapse=", "))
  all_col_names <- c(name="Route Name", road="Road", direction="Dir",
                     from_location="From", to_location="To",
                     route_type="Type", serves_zones="Zones")
  use_names <- all_col_names[names(all_col_names) %in% names(route_disp)]
  kable(route_disp, booktabs = TRUE, linesep = "", row.names = FALSE,
        col.names = use_names) %>%
    kable_styling(latex_options = c("hold_position","striped"),
                  full_width = FALSE) %>%
    column_spec(1, bold = TRUE, width = "4.5cm") %>%
    column_spec(2, width = "1.8cm")
}
```

## Current FL511 Road Conditions

```{r traffic-section, results='asis'}
if (nrow(traffic_df) == 0) {
  cat("> **No traffic incidents** currently recorded for this area.\n")
} else {
  disp_t <- traffic_df %>%
    select(any_of(c("road","type","severity","is_full_closure","description"))) %>%
    head(20)
  if ("is_full_closure" %in% names(disp_t))
    disp_t$is_full_closure <- ifelse(disp_t$is_full_closure == TRUE, "YES", "no")
  if ("description" %in% names(disp_t))
    disp_t$description <- substr(disp_t$description, 1, 60)
  kable(disp_t, booktabs = TRUE, linesep = "") %>%
    kable_styling(latex_options = c("hold_position","striped"),
                  full_width = FALSE)
}
```

```{r evac-route-traffic, results='asis'}
if (nrow(traffic_on_evac_routes) > 0) {
  cat("\n**Active incidents on designated evacuation routes:**\n\n")
  disp_er <- traffic_on_evac_routes %>%
    select(any_of(c("road","type","severity","is_full_closure","description"))) %>%
    head(10)
  if ("is_full_closure" %in% names(disp_er))
    disp_er$is_full_closure <- ifelse(disp_er$is_full_closure == TRUE, "YES", "no")
  if ("description" %in% names(disp_er))
    disp_er$description <- substr(disp_er$description, 1, 55)
  print(
    kable(disp_er, booktabs = TRUE, linesep = "") %>%
      kable_styling(latex_options = c("hold_position","striped"),
                    full_width = FALSE)
  )
} else if (n_evac_routes > 0) {
  cat("> No current traffic incidents on designated evacuation routes.\n")
}
```

## Waze Accident Hotspots Near Evacuation Corridors

```{r waze-evac-hotspots, results='asis'}
haversine_km <- function(lat1, lon1, lat2, lon2) {
  R <- 6371
  dl <- (lat2 - lat1) * pi / 180
  dn <- (lon2 - lon1) * pi / 180
  a  <- sin(dl/2)^2 + cos(lat1*pi/180) * cos(lat2*pi/180) * sin(dn/2)^2
  round(R * 2 * atan2(sqrt(a), sqrt(1 - a)), 2)
}
CORRIDOR_KM <- 15

waze_col     <- safe_mongo("waze_alerts")
waze_jam_col <- safe_mongo("waze_jams")
cutoff_ms    <- as.numeric(Sys.time() - 6 * 3600) * 1000

waze_accidents <- tryCatch({
  if (is.null(waze_col)) stop("no connection")
  q <- sprintf('{"type":"ACCIDENT","pub_millis":{"$gte":%s}}', cutoff_ms)
  r <- waze_col$find(q, fields = '{"lat":1,"lon":1,"street":1,"city":1,"subtype":1,"reliability":1,"_id":0}')
  waze_col$disconnect()
  r
}, error = function(e) {
  tryCatch(waze_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

waze_jams <- tryCatch({
  if (is.null(waze_jam_col)) stop("no connection")
  q <- sprintf('{"level":{"$gte":3},"pub_millis":{"$gte":%s}}', cutoff_ms)
  r <- waze_jam_col$find(q, fields = '{"lat":1,"lon":1,"street":1,"city":1,"level":1,"delay_sec":1,"speed_kmh":1,"_id":0}')
  waze_jam_col$disconnect()
  r
}, error = function(e) {
  tryCatch(waze_jam_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

filter_near <- function(df, lat0, lon0, km) {
  if (nrow(df) == 0 || !"lat" %in% names(df)) return(data.frame())
  df$dist_km <- mapply(haversine_km, lat0, lon0, df$lat, df$lon)
  df[df$dist_km <= km, ]
}

near_acc  <- filter_near(waze_accidents, params$lat, params$lon, CORRIDOR_KM)
near_jams <- filter_near(waze_jams,      params$lat, params$lon, CORRIDOR_KM)

if (nrow(near_acc) == 0 && nrow(near_jams) == 0) {
  cat(paste0("> No Waze accidents or heavy jams within ", CORRIDOR_KM,
             " km of this asset in the last 6 hours.\n"))
} else {
  if (nrow(near_acc) > 0) {
    cat("**Accidents near evacuation corridors (last 6 h):**\n\n")
    acc_d <- near_acc %>% arrange(dist_km) %>%
      select(any_of(c("street","city","subtype","reliability","dist_km"))) %>% head(10)
    if ("dist_km" %in% names(acc_d)) acc_d$dist_km <- paste0(round(acc_d$dist_km,1)," km")
    print(kable(acc_d, booktabs=TRUE, linesep="") %>%
      kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
      column_spec(1, width="5cm"))
  }
  if (nrow(near_jams) > 0) {
    cat("\n**Heavy traffic jams (Waze level 3+) near evacuation corridors:**\n\n")
    jam_d <- near_jams %>% arrange(dist_km) %>%
      select(any_of(c("street","city","level","delay_sec","speed_kmh","dist_km"))) %>% head(10)
    if ("delay_sec" %in% names(jam_d))
      jam_d$delay_sec <- paste0(round(jam_d$delay_sec/60,0)," min delay")
    if ("dist_km" %in% names(jam_d)) jam_d$dist_km <- paste0(round(jam_d$dist_km,1)," km")
    print(kable(jam_d, booktabs=TRUE, linesep="") %>%
      kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE))
  }
}
```

\newpage

# Nearest Airport Status

Current METAR: **`r params$nearest_airport_icao`** -- `r params$nearest_airport_name`.

```{r airport-section, results='asis'}
metar_col <- safe_mongo("airport_metar")
metar_row <- tryCatch({
  if (is.null(metar_col)) stop("no connection")
  q <- sprintf('{"icaoId":"%s"}', params$nearest_airport_icao)
  r <- metar_col$find(q, limit = 1,
    fields = '{"icaoId":1,"name":1,"temp":1,"dewp":1,"wspd":1,"wdir":1,"visib":1,"fltCat":1,"obsTime":1,"wxString":1,"_id":0}')
  metar_col$disconnect()
  r
}, error = function(e) {
  tryCatch(metar_col$disconnect(), error = function(e2) NULL)
  data.frame()
})

if (nrow(metar_row) == 0) {
  cat("> **No current METAR data** available for this station.\n")
} else {
  m      <- metar_row[1, ]
  temp_f <- if (!is.null(m$temp) && !is.na(m$temp)) round(m$temp * 9/5 + 32, 1) else NA
  obs_str <- tryCatch(
    format(as.POSIXct(m$obsTime, tz = "UTC"), "%Y-%m-%d %H:%M UTC"),
    error = function(e) "Unknown")
  apt_df <- data.frame(
    Field = c("Station","Observation Time","Temperature","Wind",
              "Visibility","Flight Category","Conditions"),
    Value = c(
      paste0(m$icaoId, " -- ", if (!is.null(m$name)) m$name else params$nearest_airport_name),
      obs_str,
      if (!is.na(temp_f)) paste0(temp_f, " F") else "N/A",
      if (!is.null(m$wspd) && !is.na(m$wspd) && m$wspd > 0)
        paste0(m$wspd, " kt / ", if (!is.null(m$wdir)) m$wdir else "?", " deg") else "Calm",
      if (!is.null(m$visib) && !is.na(m$visib)) paste0(m$visib, " sm") else "N/A",
      if (!is.null(m$fltCat) && !is.na(m$fltCat)) m$fltCat else "Unknown",
      if (!is.null(m$wxString) && !is.na(m$wxString) && nchar(m$wxString) > 0)
        m$wxString else "Clear"
    ),
    stringsAsFactors = FALSE
  )
  print(
    kable(apt_df, col.names = NULL, booktabs = TRUE, linesep = "") %>%
      kable_styling(latex_options = "hold_position", full_width = FALSE) %>%
      column_spec(1, bold = TRUE, color = FPREN_BLUE, width = "5cm") %>%
      column_spec(2, width = "10cm")
  )
}
```

\newpage

# Population & Vulnerability Analysis

Community demographics for **`r params$city`** county from US Census ACS 5-Year Estimates,
used to guide emergency messaging priorities and assess audience vulnerability.

```{r census-section, results='asis', fig.height=2.5}
# Pull census data from MongoDB fl_census collection
census_col <- safe_mongo("fl_census")
census_rec <- tryCatch({
  if (is.null(census_col)) stop("no connection")
  q <- sprintf('{"county":{"$regex":"^%s$","$options":"i"}}', params$city)
  r <- census_col$find(q, sort='{"year":-1}', limit=1,
    fields='{"county":1,"year":1,"population_total":1,"population_65plus":1,
             "population_under18":1,"population_in_poverty":1,"limited_english":1,
             "population_with_disability":1,"housing_units":1,"median_household_income":1,
             "pct_65plus":1,"pct_under18":1,"pct_poverty":1,"pct_limited_english":1,
             "pct_disability":1,"vulnerability_score":1,"_id":0}')
  census_col$disconnect()
  if (nrow(r) == 0) NULL else r[1, ]
}, error = function(e) {
  tryCatch(census_col$disconnect(), error=function(e2) NULL)
  NULL
})

if (is.null(census_rec)) {
  cat("> **No Census data available** for", params$city, "County.",
      "Run the census fetcher to populate fl_census collection.\n")
} else {
  cr <- census_rec  # shorthand
  safe_num <- function(x) { v <- tryCatch(as.numeric(x), error=function(e) NA); if(is.na(v)) 0 else v }
  pop   <- safe_num(cr$population_total)
  score <- safe_num(cr$vulnerability_score)
  v_label <- if (score >= 0.7) "Critical" else if (score >= 0.5) "High" else
             if (score >= 0.3) "Moderate" else "Low"
  v_color <- if (score >= 0.7) "red" else if (score >= 0.5) "orange" else
             if (score >= 0.3) "#0077aa" else "#2e7d32"

  # Summary table
  cen_df <- data.frame(
    Metric = c("Total Population","Age 65+","Under 18","Below Poverty Level",
               "Limited English Proficiency","With Disability","Median Household Income",
               "Housing Units","Census Dataset","Vulnerability Score"),
    Count  = c(
      format(pop, big.mark=","),
      paste0(format(safe_num(cr$population_65plus), big.mark=","), " (", cr$pct_65plus, "%)"),
      paste0(format(safe_num(cr$population_under18), big.mark=","), " (", cr$pct_under18, "%)"),
      paste0(format(safe_num(cr$population_in_poverty), big.mark=","), " (", cr$pct_poverty, "%)"),
      paste0(format(safe_num(cr$limited_english), big.mark=","), " (", cr$pct_limited_english, "%)"),
      paste0(format(safe_num(cr$population_with_disability), big.mark=","), " (", cr$pct_disability, "%)"),
      paste0("$", format(safe_num(cr$median_household_income), big.mark=",")),
      format(safe_num(cr$housing_units), big.mark=","),
      as.character(cr$year %||% "ACS 5-Year"),
      paste0(round(score, 3), " / 1.0 (", v_label, ")")
    ),
    stringsAsFactors = FALSE
  )

  print(
    kable(cen_df, col.names=c("Demographic Metric","Value"),
          booktabs=TRUE, linesep="") %>%
      kable_styling(latex_options=c("hold_position","striped"), full_width=FALSE) %>%
      column_spec(1, bold=TRUE, color=FPREN_BLUE, width="7cm") %>%
      column_spec(2, width="8cm") %>%
      row_spec(nrow(cen_df), bold=TRUE, color=v_color)
  )

  # Vulnerability bar chart
  vul_df <- data.frame(
    Group = c("Age 65+","Under 18","Poverty","Lim. English","Disability"),
    Pct   = c(safe_num(cr$pct_65plus), safe_num(cr$pct_under18),
              safe_num(cr$pct_poverty), safe_num(cr$pct_limited_english),
              safe_num(cr$pct_disability))
  )
  colors <- c("#e07020","#0077aa","#c0392b","#8e44ad","#16a085")
  p_cen <- ggplot(vul_df, aes(x=reorder(Group, Pct), y=Pct, fill=Group)) +
    geom_col(width=0.6, show.legend=FALSE) +
    scale_fill_manual(values=colors) +
    coord_flip() +
    labs(title=paste0(params$city, " County Vulnerable Population Groups (%)"),
         x=NULL, y="% of Total Population") +
    theme_minimal(base_size=10) +
    theme(plot.title=element_text(color=FPREN_BLUE, face="bold", size=10))
  print(p_cen)

  # AI BCP demographic narrative
  cat("\n\n**AI-Generated Demographic Analysis (LiteLLM):**\n\n")
  ai_text <- tryCatch({
    # Call census AI analyzer via system2
    script <- "/home/ufuser/Fpren-main/weather_rss/census_ai_analyzer.py"
    if (file.exists(script)) {
      cmd_args <- c("-c", sprintf(
        'import sys; sys.path.insert(0,"/home/ufuser/Fpren-main/weather_rss"); sys.path.insert(0,"/home/ufuser/Fpren-main");
import census_ai_analyzer as ca
print(ca.analyze_bcp_demographics("%s", "%s"))',
        params$city, params$asset_name
      ))
      result <- system2("python3", args=cmd_args, stdout=TRUE, stderr=FALSE, timeout=30)
      if (length(result) > 0) paste(result, collapse=" ") else ""
    } else ""
  }, error=function(e) "")

  if (nchar(ai_text) > 0) {
    cat("> *", ai_text, "*\n\n")
  } else {
    # Fallback narrative
    cat(sprintf(
      "> *%s County has a vulnerability score of %.3f (%s), with %.1f%% of the population over age 65 and %.1f%% below the poverty line. These groups depend heavily on emergency radio broadcasts and may lack alternative information sources during a disaster.*\n\n",
      params$city, score, v_label,
      safe_num(cr$pct_65plus), safe_num(cr$pct_poverty)
    ))
  }
}
```

\newpage

# Business Continuity Recommendations

```{r recommendations, results='asis'}
recs <- list()
if (alert_risk == "HIGH")
  recs <- c(recs, "**HIGH ALERT RISK:** Multiple Extreme/Severe NWS alerts recently. Activate emergency protocols immediately.")
if (alert_risk == "MODERATE")
  recs <- c(recs, "**MODERATE ALERT RISK:** Some significant NWS alerts recorded. Monitor NWS feed closely.")
if (wx_risk == "HIGH")
  recs <- c(recs, "**HIGH WEATHER RISK:** High wind events or frequent IFR/LIFR detected. Inspect building integrity, backup power, and antenna mounts.")
if (wx_risk == "MODERATE")
  recs <- c(recs, "**MODERATE WEATHER RISK:** Elevated winds or reduced visibility observed. Verify generator fuel and backup communications.")
if (traffic_risk == "HIGH")
  recs <- c(recs, "**HIGH TRAFFIC RISK:** Full road closures detected. Identify and test alternate access routes immediately.")
if (traffic_risk == "MODERATE")
  recs <- c(recs, "**MODERATE TRAFFIC RISK:** Road incidents in area. Brief personnel on alternate routes.")
if (evac_risk == "HIGH" && !is.na(highest_zone))
  recs <- c(recs, paste0("**EVACUATION ZONE A ASSET:** This facility is in the highest hurricane evacuation zone. ",
    "Pre-position a remote broadcast capability and ensure staff know evacuation routes: ",
    if (n_evac_routes > 0) paste(head(evac_routes_df$name, 2), collapse="; ") else "see county EM plan."))
if (evac_risk == "MODERATE" && !is.na(highest_zone))
  recs <- c(recs, paste0("**EVACUATION ZONE ", highest_zone, " ASSET:** Brief all personnel on primary evacuation routes for this county. ",
    "Monitor National Hurricane Center advisories. Primary routes: ",
    if (n_evac_routes > 0) paste(head(evac_routes_df$name[evac_routes_df$route_type=="Primary"], 2), collapse="; ") else "see county EM plan."))
if (nrow(traffic_on_evac_routes) > 0)
  recs <- c(recs, paste0("**EVACUATION ROUTE INCIDENT:** ",
    nrow(traffic_on_evac_routes), " active FL511 incident(s) on designated evacuation routes. ",
    "Identify alternate routes before activating evacuation plan."))
recs <- c(recs,
  "Verify UPS/generator tested and fueled for 72-hour autonomous operation.",
  "Confirm all 9 Icecast zone mounts are streaming on port 8000.",
  "Ensure MongoDB backups are current -- daily backup to off-site storage recommended.",
  "Verify SMTP and Twilio credentials are valid for staff notifications.",
  paste0("Nearest aviation hub: **", params$nearest_airport_icao, "** (", params$nearest_airport_name, ") -- monitor FAA NOTAMs."),
  "Contact UF IT (352-392-4357) for network/firewall issues affecting stream delivery."
)
if (overall_risk == "LOW") {
  recs <- c(recs, "**Overall: LOW risk.** Normal operations. Maintain regular monitoring schedule.")
} else if (overall_risk == "MODERATE") {
  recs <- c(recs, "**Overall: MODERATE risk.** Increase monitoring frequency. Brief on-call staff.")
} else {
  recs <- c(recs, "**Overall: HIGH risk.** Activate full BCP. Contact FPREN admin and UF Emergency Management.")
}
for (i in seq_along(recs)) cat(paste0(i, ". ", recs[[i]], "\n\n"))
```

\newpage

# Recovery Timeline

```{r recovery-timeline, results='asis'}
timeline <- data.frame(
  Phase  = c(rep("Immediate (0-4 h)", 3), rep("Short-term (4-24 h)", 3),
             rep("Medium-term (1-7 d)", 3), rep("Long-term (7-30 d)", 2)),
  Action = c(
    "Notify FPREN admin and activate emergency contact tree",
    "Assess physical damage to transmitter, antennas, and server hardware",
    "Switch Icecast mounts to backup server/IP if available",
    "Restore MongoDB from most recent backup",
    "Verify all 9 zone streams are live on port 8000",
    "Confirm beacon-ipaws-fetcher and beacon-obs-fetcher are running",
    "Replace or repair damaged hardware via UF procurement",
    "Full system test -- generate test TTS across all zones",
    "Document incident in FPREN incident log; notify stakeholders",
    "Review and update this BCP based on lessons learned",
    "Submit incident report to UF IT and oversight bodies"
  ),
  Owner  = c("Admin","On-site","Admin/IT","Admin","Admin","Admin",
             "UF IT","Admin","Admin","Admin","Admin"),
  Done   = rep("[ ]", 11),
  stringsAsFactors = FALSE
)
kable(timeline, booktabs = TRUE, linesep = "",
      col.names = c("Phase","Action","Owner","Done")) %>%
  kable_styling(latex_options = c("hold_position","striped","scale_down"),
                full_width = FALSE) %>%
  column_spec(1, width = "3.2cm", bold = TRUE, color = FPREN_BLUE) %>%
  column_spec(2, width = "8cm") %>%
  column_spec(3, width = "2.2cm") %>%
  column_spec(4, width = "1cm")
```

\newpage

# Emergency Contacts

```{r emergency-contacts, results='asis'}
# ── Core FPREN / UF contacts ─────────────────────────────────────────────────
contacts <- data.frame(
  Role = c("FPREN Administrator","UF IT Help Desk","UF Emergency Management",
           "UF Police Department","National Hurricane Center",
           "NWS Jacksonville (FL alerts)","NOAA Weather Radio"),
  Address = c(
    "Weimer Hall, 1885 Stadium Rd, Gainesville FL 32611",
    "132 Hub, University of Florida, Gainesville FL 32611",
    "222 Tigert Hall, Gainesville FL 32611",
    "1555 Museum Rd, Gainesville FL 32611",
    "11691 SW 17th St, Miami FL 33165",
    "4 Aviation Center Pkwy, Jacksonville FL 32218",
    "1325 East-West Hwy, Silver Spring MD 20910"
  ),
  Phone_Email = c(
    "lawrence.bornace@ufl.edu",
    "(352) 392-4357 | helpdesk@ufl.edu",
    "(352) 392-1111 | ufl.edu/emergency",
    "(352) 392-1111",
    "(305) 229-4470 | nhc.noaa.gov",
    "(904) 741-4311 | weather.gov/jax",
    "1610 kHz / WXL-52"
  ),
  stringsAsFactors = FALSE
)
kable(contacts, col.names = c("Role / Organization","Address","Phone / Contact"),
      booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("hold_position","striped","scale_down"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, color = FPREN_BLUE, width = "4.5cm") %>%
  column_spec(2, width = "5.5cm") %>%
  column_spec(3, width = "4cm")
```

## County Emergency Management & Law Enforcement

```{r county-em-contacts, results='asis'}
county_em <- data.frame(
  Agency = c(
    "Alachua County Emergency Management",
    "Leon County Emergency Management",
    "Hillsborough County Emergency Management",
    "Miami-Dade County Emergency Management",
    "Orange County Emergency Management",
    "Duval County Emergency Management",
    "Pinellas County Emergency Management",
    "Palm Beach County Emergency Management",
    "Broward County Emergency Management"
  ),
  Address = c(
    "420 NE 1st St, Gainesville FL 32601",
    "1301 Rankin Ave, Tallahassee FL 32308",
    "2701 N 50th St, Tampa FL 33605",
    "9300 NW 41st St, Doral FL 33178",
    "6590 Amory Ct, Winter Park FL 32792",
    "515 N Julia St, Jacksonville FL 32202",
    "400 S Fort Harrison Ave, Clearwater FL 33756",
    "20 S Military Trail, West Palm Beach FL 33415",
    "201 NW 84th Ave, Plantation FL 33324"
  ),
  Phone = c(
    "(352) 264-6500","(850) 606-5000","(813) 272-6900",
    "(305) 468-5400","(407) 836-9140","(904) 630-4000",
    "(727) 464-3800","(561) 712-6400","(954) 831-3900"
  ),
  stringsAsFactors = FALSE
)
kable(county_em, booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("hold_position","striped","scale_down"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, width = "5cm") %>%
  column_spec(2, width = "5.5cm") %>%
  column_spec(3, width = "2.5cm")
```

## State & Federal Agencies

```{r state-agencies, results='asis'}
state_ag <- data.frame(
  Agency = c(
    "FL Division of Emergency Management",
    "FL Dept of Law Enforcement (FDLE)",
    "FL Dept of Transportation — District 2",
    "FL National Guard Joint Operations Center",
    "FL Dept of Health — Emergency Operations",
    "FEMA Region 4 (Southeast)",
    "FBI Tampa Field Office",
    "American Red Cross — FL"
  ),
  Address = c(
    "2555 Shumard Oak Blvd, Tallahassee FL 32399",
    "2331 Phillips Rd, Tallahassee FL 32308",
    "1109 S Marion Ave, Lake City FL 32025",
    "82 Marine St, St Augustine FL 32084",
    "4052 Bald Cypress Way, Tallahassee FL 32399",
    "3003 Chamblee Tucker Rd, Atlanta GA 30341",
    "5525 W Gray St, Tampa FL 33609",
    "6100 Lake Ellenor Dr, Orlando FL 32809"
  ),
  Phone = c(
    "(850) 413-9969","(850) 410-7000","(386) 961-7800",
    "(904) 823-0100","(850) 245-4444","(770) 220-5200",
    "(813) 253-1000","(407) 894-4141"
  ),
  stringsAsFactors = FALSE
)
kable(state_ag, booktabs = TRUE, linesep = "") %>%
  kable_styling(latex_options = c("hold_position","striped","scale_down"), full_width = FALSE) %>%
  column_spec(1, bold = TRUE, width = "5.5cm") %>%
  column_spec(2, width = "5cm") %>%
  column_spec(3, width = "2.5cm")
```

```{r role-specific-contacts, results='asis'}
prof <- params$profession

role_contacts <- list(
  "Broadcast Engineer" = data.frame(
    Agency  = c("FCC Emergency Communications","Society of Broadcast Engineers Ch.28",
                "NPR Emergency Operations","EAS LPFM Emergency Coordinator",
                "UF College of Journalism (WUFT)"),
    Contact = c("(888) 225-5322 | fcc.gov",
                "sbe.org/chapters/28",
                "(202) 513-2000",
                "Contact via state EAS plan",
                "(352) 392-0466 | wuft.org"),
    stringsAsFactors = FALSE),
  "Broadcast Administrator" = data.frame(
    Agency  = c("FCC Emergency Desk","Corporation for Public Broadcasting",
                "NPR Newsdesk Emergency","UF Communications & Marketing"),
    Contact = c("(888) 225-5322 | fcc.gov",
                "(202) 879-9600",
                "(202) 513-2000",
                "(352) 392-0186"),
    stringsAsFactors = FALSE),
  "County Emergency Manager" = data.frame(
    Agency  = c("FL DEM Director","FL Emergency Alert Coordinator",
                "FEMA Individual Assistance","FEMA National Response Coordination"),
    Contact = c("(850) 413-9969 | floridadisaster.org",
                "(850) 413-9900",
                "(800) 621-3362",
                "(202) 646-4600"),
    stringsAsFactors = FALSE),
  "Police Chief" = data.frame(
    Agency  = c("FL Dept of Law Enforcement","Florida Highway Patrol",
                "FBI Crisis Response","ATF Jacksonville"),
    Contact = c("(850) 410-7000",
                "(850) 617-2000",
                "(800) CALL-FBI",
                "(904) 724-7330"),
    stringsAsFactors = FALSE),
  "EOC Coordinator" = data.frame(
    Agency  = c("FL State EOC (24/7)","FEMA Region 4 EOC","National Emergency Management Association",
                "FL Emergency Communications State Director"),
    Contact = c("(850) 413-9900",
                "(770) 220-5200",
                "nema.org",
                "(850) 413-9900"),
    stringsAsFactors = FALSE),
  "IT/Systems Administrator" = data.frame(
    Agency  = c("UF IT Security (UFIT)","UF Network Operations Center",
                "FL Digital Service (BITS)","CISA (Cybersecurity & Infrastructure)"),
    Contact = c("(352) 273-1344 | security.it.ufl.edu",
                "(352) 392-4357",
                "(850) 577-0120",
                "(888) 282-0870 | cisa.gov"),
    stringsAsFactors = FALSE),
  "Facility Manager" = data.frame(
    Agency  = c("UF Facilities Services Emergency","GRU Emergency (power/gas)",
                "Gainesville Regional Utilities","UF Environmental Health & Safety"),
    Contact = c("(352) 392-1121",
                "(352) 334-3400",
                "(352) 334-3434",
                "(352) 392-1591"),
    stringsAsFactors = FALSE)
)

specific <- role_contacts[[prof]]
if (!is.null(specific)) {
  cat(paste0("\n## Role-Specific Contacts: ", prof, "\n\n"))
  print(
    kable(specific, booktabs = TRUE, linesep = "",
          col.names = c("Agency / Organization","Phone / Contact")) %>%
      kable_styling(latex_options = c("hold_position","striped"), full_width = FALSE) %>%
      column_spec(1, bold = TRUE, color = FPREN_BLUE, width = "7cm") %>%
      column_spec(2, width = "7cm")
  )
} else {
  cat(paste0("> No role-specific contacts defined for: **", prof, "**.",
             " Contact Alachua County Emergency Management at (352) 264-6500",
             " and FL Division of Emergency Management at (850) 413-9969.\n"))
}
```


\newpage

# SMS Emergency Action Checklist

Role-based action items for **`r params$profession`** across all emergency phases.
These lists are also delivered as SMS blasts from the FPREN dashboard.

```{r sms-checklist, results='asis'}
sms_col <- safe_mongo("emergency_roles_config")

get_todos_rmd <- function(role, phase) {
  tryCatch({
    if (is.null(sms_col)) return(character(0))
    q <- sprintf('{"role":"%s","phase":"%s"}', gsub('"', '\\\\"', role), phase)
    r <- sms_col$find(q, fields = '{"todos":1,"_id":0}')
    if (nrow(r) == 0 || is.null(r$todos)) return(character(0))
    t <- r$todos[[1]]
    if (is.list(t)) unlist(t) else as.character(t)
  }, error = function(e) character(0))
}

tb <- get_todos_rmd(params$profession, "before")
td <- get_todos_rmd(params$profession, "during")
ta <- get_todos_rmd(params$profession, "after")
tryCatch(sms_col$disconnect(), error = function(e) NULL)

if (length(tb) == 0 && length(td) == 0 && length(ta) == 0) {
  cat(paste0("> No SMS action checklist defined for **", params$profession, "**.",
             " Configure in the FPREN dashboard — Config tab > Emergency SMS.\n"))
} else {
  max_r <- max(length(tb), length(td), length(ta), 1)
  pad   <- function(x, n) c(x, rep("", n - length(x)))
  tb2 <- pad(tb, max_r); td2 <- pad(td, max_r); ta2 <- pad(ta, max_r)
  check_df <- data.frame(
    `Before Event` = ifelse(nchar(tb2)>0, paste0("[ ] ", tb2), ""),
    `During Event` = ifelse(nchar(td2)>0, paste0("[ ] ", td2), ""),
    `After Event`  = ifelse(nchar(ta2)>0, paste0("[ ] ", ta2), ""),
    check.names    = FALSE, stringsAsFactors = FALSE
  )
  check_df <- check_df[rowSums(nchar(trimws(as.matrix(check_df))) > 0) > 0, ]
  if (nrow(check_df) > 0) {
    print(
      kable(check_df, booktabs = TRUE, linesep = "",
            col.names = c("Before Event","During Event","After Event")) %>%
        kable_styling(latex_options = c("hold_position","striped","scale_down"),
                      full_width = TRUE) %>%
        column_spec(1:3, width = "5.5cm")
    )
  }
}
```

\newpage

# Asset Network & Backup Sites

```{r asset-network, results='asis'}
library(jsonlite)
other_assets <- tryCatch(
  jsonlite::fromJSON(params$other_assets_json, simplifyDataFrame=TRUE),
  error = function(e) data.frame()
)

# Haversine distance in miles
.haversine_mi <- function(lat1, lon1, lat2, lon2) {
  R <- 3958.8
  d_lat <- (lat2 - lat1) * pi / 180
  d_lon <- (lon2 - lon1) * pi / 180
  a <- sin(d_lat/2)^2 + cos(lat1*pi/180)*cos(lat2*pi/180)*sin(d_lon/2)^2
  round(R * 2 * atan2(sqrt(a), sqrt(1-a)), 1)
}

if (!is.data.frame(other_assets) || nrow(other_assets) == 0) {
  cat("> No additional assets registered for this user. Add assets in the Config tab to include backup/alternate site analysis.\n")
} else {
  this_lat <- params$lat
  this_lon <- params$lon

  # Build display table
  tbl <- do.call(rbind, lapply(seq_len(nrow(other_assets)), function(i) {
    a <- other_assets[i, ]
    lat2 <- tryCatch(as.numeric(a$lat), error=function(e) NA)
    lon2 <- tryCatch(as.numeric(a$lon), error=function(e) NA)
    dist <- if (!is.na(lat2) && !is.na(lon2)) .haversine_mi(this_lat, this_lon, lat2, lon2) else NA
    pri  <- if ("priority" %in% names(a) && !is.na(a$priority)) as.integer(a$priority) else i
    data.frame(
      Priority   = pri,
      Name       = as.character(a$asset_name %||% "—"),
      Type       = as.character(a$asset_type %||% "—"),
      Location   = paste0(as.character(a$city %||% ""), ", ", as.character(a$zip %||% "")),
      Airport    = as.character(a$nearest_airport_icao %||% "—"),
      `Dist (mi)` = ifelse(is.na(dist), "—", as.character(dist)),
      Notes      = as.character(a$notes %||% ""),
      stringsAsFactors = FALSE, check.names = FALSE
    )
  }))
  tbl <- tbl[order(tbl$Priority), ]

  cat(paste0("This BCP covers **", params$asset_name, "** (Priority ", 
    if ("priority" %in% names(other_assets)) "1" else "—",
    "). The user has **", nrow(other_assets),
    "** additional registered asset(s) that serve as backup or alternate sites.\n\n"))

  knitr::kable(tbl, booktabs=TRUE, row.names=FALSE,
    caption="User's other registered assets — potential backup/alternate sites") %>%
    kableExtra::kable_styling(
      latex_options=c("striped","hold_position","scale_down"), font_size=9) %>%
    kableExtra::column_spec(2, bold=TRUE) %>%
    kableExtra::column_spec(6, bold=TRUE)
}
```

```{r asset-network-detail, results='asis'}
if (is.data.frame(other_assets) && nrow(other_assets) > 0) {
  cat("## Site Details\n\n")
  for (i in seq_len(nrow(other_assets))) {
    a <- other_assets[i, ]
    lat2 <- tryCatch(as.numeric(a$lat), error=function(e) NA)
    lon2 <- tryCatch(as.numeric(a$lon), error=function(e) NA)
    dist <- if (!is.na(lat2) && !is.na(lon2)) .haversine_mi(params$lat, params$lon, lat2, lon2) else NA
    dist_str <- if (is.na(dist)) "distance unknown" else paste0(dist, " miles from this facility")
    cat(paste0(
      "**", as.character(a$asset_name %||% "Unknown"), "**",
      " (", as.character(a$asset_type %||% "Facility"), ")",
      " — ", dist_str, "\\\\\n",
      "Address: ", as.character(a$address %||% "—"), "\\\\\n",
      "Nearest Airport: ", as.character(a$nearest_airport_icao %||% "—"),
      " — ", as.character(a$nearest_airport_name %||% ""), "\\\\\n"
    ))
    if (!is.null(a$notes) && nchar(as.character(a$notes %||% "")) > 0)
      cat(paste0("Notes: *", as.character(a$notes), "*\\\\\n"))
    cat("\n")
  }
}
```

\vspace{16pt}
\begin{center}
\textcolor{fprenblue}{\rule{\linewidth}{1pt}}\\
\vspace{4pt}
{\small\textit{Generated by FPREN Automated Reporting -- `r format(Sys.time(), "%Y-%m-%d %H:%M ET")`}}\\
{\small\textit{Asset: `r params$asset_name` | User: `r params$username`}}\\
{\small Florida Public Radio Emergency Network -- University of Florida}
\end{center}
