---
title: "FPREN Alert Population Impact Report"
subtitle: "Florida Public Radio Emergency Network — Census & Demographics Analysis"
date: "Generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`"
geometry: "margin=1in"
output:
  pdf_document:
    toc: false
    latex_engine: xelatex
    keep_tex: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{xcolor}
  - \usepackage{longtable}
  - \definecolor{fprenblue}{RGB}{0, 70, 127}
  - \definecolor{warnyellow}{RGB}{243, 156, 18}
  - \definecolor{dangerred}{RGB}{192, 57, 43}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\textcolor{fprenblue}{\textbf{FPREN}}}
  - \fancyhead[C]{\textcolor{fprenblue}{Alert Population Impact}}
  - \fancyhead[R]{\textcolor{gray}{Census \& Demographics}}
  - \renewcommand{\headrulewidth}{0.4pt}
params:
  alert_event:       "Unknown Event"
  alert_area:        ""
  alert_severity:    ""
  alert_headline:    ""
  alert_description: ""
  total_population:  0
  counties_json:     "{}"
  ai_analysis:       ""
  mongo_uri:         "mongodb://localhost:27017/"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)
suppressPackageStartupMessages({
  library(knitr)
  library(kableExtra)
  library(dplyr)
  library(jsonlite)
})

counties_data <- tryCatch(fromJSON(params$counties_json), error=function(e) list())

sev_color <- switch(tolower(params$alert_severity %||% ""),
  extreme = "\\textcolor{dangerred}{\\textbf{EXTREME}}",
  severe  = "\\textcolor{dangerred}{\\textbf{SEVERE}}",
  moderate= "\\textcolor{warnyellow}{\\textbf{MODERATE}}",
  "\\textbf{UNKNOWN}"
)
```

\begin{center}
{\Large \textcolor{fprenblue}{\textbf{`r params$alert_event`}}}\\[4pt]
{\normalsize Severity: `r sev_color`}\\[2pt]
{\small `r params$alert_area`}
\end{center}

\vspace{6pt}
\hrule
\vspace{10pt}

# Alert Summary

```{r alert-summary, results='asis'}
cat(paste0(
  "| Field | Detail |\n",
  "|---|---|\n",
  "| **Event** | ", params$alert_event, " |\n",
  "| **Severity** | ", params$alert_severity, " |\n",
  "| **Area** | ", params$alert_area, " |\n",
  "| **Headline** | ", gsub("\\|","\\\\|", params$alert_headline), " |\n"
))
```

```{r description, results='asis'}
if (nchar(params$alert_description) > 0) {
  cat("\n**Alert Description:**\n\n")
  cat("\\begin{quote}\n")
  cat(gsub("\n", "  \n", params$alert_description))
  cat("\n\\end{quote}\n")
}
```

\newpage

# Population at Risk

\begin{center}
{\Huge \textcolor{dangerred}{\textbf{`r format(as.integer(params$total_population), big.mark=",")`}}}\\[4pt]
{\large Total population in affected counties}
\end{center}

\vspace{12pt}

## County-by-County Breakdown

```{r county-table, results='asis'}
if (length(counties_data) > 0 && is.list(counties_data)) {
  rows <- lapply(names(counties_data), function(county) {
    d <- counties_data[[county]]
    data.frame(
      County            = county,
      Population        = format(as.integer(d$population_total %||% 0), big.mark=","),
      "Age 65+"         = paste0(round(d$pct_65plus  %||% 0, 1), "%"),
      Poverty           = paste0(round(d$pct_poverty  %||% 0, 1), "%"),
      "Vuln. Score"     = round(d$vulnerability_score %||% 0, 3),
      "Risk Level"      = d$vulnerability_label %||% "—",
      stringsAsFactors  = FALSE,
      check.names       = FALSE
    )
  })
  df <- do.call(rbind, rows)
  kable(df, booktabs=TRUE, align=c("l","r","r","r","r","l"),
        caption="Census demographics for affected counties (ACS 5-year estimates)") %>%
    kable_styling(latex_options=c("striped","hold_position"), font_size=10) %>%
    column_spec(6, bold=TRUE,
      color = ifelse(df[["Risk Level"]] %in% c("Critical","High"), "white", "black"),
      background = ifelse(df[["Risk Level"]] == "Critical", "#c0392b",
                   ifelse(df[["Risk Level"]] == "High",     "#e67e22",
                   ifelse(df[["Risk Level"]] == "Moderate", "#f1c40f", "#27ae60"))))
} else {
  cat("> No county census data available.\n")
}
```

\newpage

# AI Population Impact Assessment

```{r ai-analysis, results='asis'}
analysis <- params$ai_analysis
if (nchar(analysis) > 0 && analysis != "No census data available.") {
  # Split by double newline (one paragraph per county)
  paras <- strsplit(analysis, "\n\n")[[1]]
  for (p in paras) {
    parts <- strsplit(p, ": ", fixed=TRUE)[[1]]
    if (length(parts) >= 2) {
      cat(paste0("**", parts[1], ":** ", paste(parts[-1], collapse=": "), "\n\n"))
    } else {
      cat(paste0(p, "\n\n"))
    }
  }
} else {
  cat("> AI analysis was not available for this alert.\n")
}
```

---

*Report generated by FPREN Census & Demographics module.*
*Data source: US Census Bureau ACS 5-year estimates via MongoDB `weather_rss.fl_census`.*
*NWS alert data via `weather_rss.nws_alerts`.*
*Server: `r Sys.info()[["nodename"]]` | R `r R.version.string`*
