---
title: "FPREN County Alert Report"
subtitle: "Florida Public Radio Emergency Network — `r params$county_name` County"
date: "Generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`"
geometry: "margin=1in"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    latex_engine: xelatex
    keep_tex: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{xcolor}
  - \usepackage{longtable}
  - \definecolor{fprenblue}{RGB}{0, 70, 127}
  - \definecolor{extremered}{RGB}{192, 57, 43}
  - \definecolor{severeorange}{RGB}{230, 126, 34}
  - \definecolor{moderateyellow}{RGB}{243, 156, 18}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\textcolor{fprenblue}{\textbf{FPREN}}}
  - \fancyhead[C]{\textcolor{fprenblue}{County Alert Report}}
  - \fancyhead[R]{\textcolor{gray}{`r params$county_name` County}}
  - \renewcommand{\headrulewidth}{0.4pt}
params:
  county_name: "Alachua"
  date: ""
  mongo_uri: "mongodb://localhost:27017/"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE
)

suppressPackageStartupMessages({
  library(mongolite)
  library(dplyr)
  library(lubridate)
  library(knitr)
  library(kableExtra)
})

get_col <- function(collection) {
  tryCatch(
    mongo(collection = collection, db = "weather_rss", url = params$mongo_uri),
    error = function(e) NULL
  )
}

county      <- params$county_name
report_date <- if (nchar(params$date) > 0) params$date else format(Sys.Date(), "%Y-%m-%d")

# Build slug for source match (mirrors county_rss_fetcher.py)
slug <- tolower(gsub("[. ]", "_", gsub("\\.", "", county)))

# Query: area_desc contains county name OR source = county_nws:{slug}
query <- sprintf(
  '{"$or":[{"area_desc":{"$regex":"%s","$options":"i"}},{"source":"county_nws:%s"}]}',
  county, slug
)

col    <- get_col("nws_alerts")
alerts <- if (!is.null(col)) {
  tryCatch({
    df <- col$find(query,
      fields = '{"alert_id":1,"event":1,"headline":1,"severity":1,"urgency":1,
                 "area_desc":1,"source":1,"sent":1,"expires":1,
                 "description":1,"fetched_at":1,"_id":0}')
    col$disconnect()
    df
  }, error = function(e) { tryCatch(col$disconnect(), error=function(e2) NULL); data.frame() })
} else data.frame()

# Normalise timestamps to ET display strings
fmt_ts <- function(x) {
  if (is.null(x) || length(x) == 0) return(rep("—", length(x)))
  sapply(x, function(v) {
    tryCatch(
      format(as.POSIXct(v, tz = "UTC"), "%b %d %H:%M ET",
             usetz = FALSE),
      error = function(e) as.character(v)
    )
  })
}

n_total   <- nrow(alerts)
n_extreme <- if (n_total > 0) sum(tolower(alerts$severity) %in% c("extreme","severe"), na.rm=TRUE) else 0
n_mod     <- if (n_total > 0) sum(tolower(alerts$severity) == "moderate", na.rm=TRUE) else 0
n_minor   <- if (n_total > 0) sum(tolower(alerts$severity) == "minor", na.rm=TRUE) else 0

# Check zone audio files
wav_col  <- get_col("zone_alert_wavs")
n_wavs   <- 0L
if (!is.null(wav_col)) {
  tryCatch({
    wq <- sprintf('{"zone":{"$in":["%s","all_florida"]}}', slug)
    wdf <- wav_col$find(wq, fields='{"_id":0,"zone":1}')
    wav_col$disconnect()
    n_wavs <- nrow(wdf)
  }, error = function(e) tryCatch(wav_col$disconnect(), error=function(e2) NULL))
}
```

\newpage

# Executive Summary

**County:** `r county`
**Report Date:** `r report_date`
**Generated:** `r format(Sys.time(), "%Y-%m-%d %H:%M:%S UTC")`
**Data Source:** NOAA/NWS via FPREN MongoDB (`nws_alerts`)

---

```{r summary-table, results='asis'}
cat(paste0(
  "| Metric | Value |\n",
  "|--------|-------|\n",
  "| **County** | ", county, " |\n",
  "| **Total Active Alerts** | **", n_total, "** |\n",
  "| Extreme / Severe | **", n_extreme, "** |\n",
  "| Moderate | ", n_mod, " |\n",
  "| Minor | ", n_minor, " |\n",
  "| Zone Audio Files | ", n_wavs, " |\n"
))
```

```{r no-alerts, results='asis'}
if (n_total == 0) {
  cat("\n> **No active alerts found for ", county, " County at time of report generation.**\n", sep="")
  knitr::knit_exit()
}
```

\newpage

# Active Alerts Summary

```{r alerts-table}
if (n_total > 0) {
  display <- alerts %>%
    select(any_of(c("event","severity","area_desc","sent","expires","source"))) %>%
    mutate(
      sent    = fmt_ts(sent),
      expires = fmt_ts(expires),
      severity = factor(severity,
        levels = c("Extreme","Severe","Moderate","Minor","Unknown"), exclude = NULL)
    ) %>%
    arrange(severity) %>%
    rename_with(~ c("Event","Severity","Area","Issued","Expires","Source")[seq_along(.)],
                everything())

  kable(display, booktabs = TRUE, longtable = TRUE,
        caption = paste0("All active NWS alerts for ", county, " County")) %>%
    kable_styling(
      latex_options = c("striped","hold_position","repeat_header"),
      font_size = 8
    ) %>%
    row_spec(which(display$Severity %in% c("Extreme","Severe")),
             bold = TRUE, color = "white", background = "#c0392b") %>%
    row_spec(which(display$Severity == "Moderate"),
             bold = TRUE, color = "black", background = "#f39c12")
}
```

\newpage

# Alert Details

```{r alert-details, results='asis'}
if (n_total > 0) {
  for (i in seq_len(nrow(alerts))) {
    a <- alerts[i, ]

    sev_label <- toupper(as.character(a$severity %||% "UNKNOWN"))
    event_str <- as.character(a$event     %||% "Unknown Event")
    hl_str    <- as.character(a$headline  %||% event_str)
    area_str  <- as.character(a$area_desc %||% "—")
    src_str   <- as.character(a$source    %||% "—")
    sent_str  <- fmt_ts(a$sent)
    exp_str   <- fmt_ts(a$expires)
    desc_str  <- as.character(a$description %||% "No description available.")
    # Sanitise for LaTeX
    clean <- function(x) gsub("([#$%&_{}~^\\\\])", "\\\\\\1", x)

    cat(sprintf(
      "## Alert %d: %s\n\n",
      i, clean(event_str)
    ))
    cat(paste0(
      "**Severity:** ", sev_label, "  \n",
      "**Headline:** ", clean(hl_str), "  \n",
      "**Area:** ", clean(area_str), "  \n",
      "**Source:** ", clean(src_str), "  \n",
      "**Issued:** ", sent_str, "  \n",
      "**Expires:** ", exp_str, "\n\n",
      "**Description:**\n\n",
      "\\begin{quote}\n",
      gsub("\n", "  \n", clean(desc_str)),
      "\n\\end{quote}\n\n",
      "---\n\n"
    ))
  }
}
```

\newpage

# Severity Distribution

```{r severity-dist, results='asis'}
if (n_total > 0) {
  sev_tbl <- alerts %>%
    mutate(severity = as.character(severity)) %>%
    count(severity, name = "Count") %>%
    mutate(
      Pct = paste0(round(Count / n_total * 100, 1), "%"),
      severity = factor(severity,
        levels = c("Extreme","Severe","Moderate","Minor","Unknown"), exclude = NULL)
    ) %>%
    arrange(severity) %>%
    rename(Severity = severity)

  kable(sev_tbl, booktabs = TRUE, align = c("l","r","r"),
        caption = "Alert count by severity") %>%
    kable_styling(latex_options = c("striped","hold_position"), font_size = 10)
}
```

---

*Report generated by FPREN R reporting system.*
*Data source: NOAA/NWS via MongoDB `weather_rss.nws_alerts`.*
*Server: `r Sys.info()[["nodename"]]` | R `r R.version.string`*
