---
title: "FPREN Connectivity & Accessibility Report"
subtitle: "Port, Service, and API Reachability — UF VM 128.227.67.234"
date: "`r format(Sys.time(), '%B %d, %Y %I:%M %p %Z')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
geometry: "left=0.85in,right=0.85in,top=0.9in,bottom=0.9in"
header-includes:
  - \usepackage{booktabs}
  - \usepackage{colortbl}
  - \usepackage{xcolor}
  - \renewcommand{\arraystretch}{1.2}
params:
  mongo_uri: "mongodb://localhost:27017/"
  checker_script: "/home/ufuser/Fpren-main/scripts/check_fpren_access.py"
  python_bin: "/home/ufuser/Fpren-main/venv/bin/python3"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(jsonlite)
library(dplyr)
library(knitr)
library(kableExtra)

trunc_str <- function(x, n = 52) {
  ifelse(is.na(x) | x == "NULL" | x == "NA", "—",
    ifelse(nchar(as.character(x)) > n,
           paste0(substr(as.character(x), 1, n), "\u2026"),
           as.character(x)))
}
```

```{r run_checker}
raw <- tryCatch(
  system2(params$python_bin,
          args    = c(params$checker_script, "--pretty"),
          stdout  = TRUE, stderr = FALSE, timeout = 120),
  error = function(e) NULL
)

if (is.null(raw) || length(raw) == 0) {
  data <- list(results = data.frame(), total = 0,
               reachable = 0, blocked = 0, refused = 0, errors = 0,
               generated_at = "N/A")
} else {
  data <- tryCatch(fromJSON(paste(raw, collapse = "\n")),
                   error = function(e) list(results = data.frame()))
}

df <- if (is.data.frame(data$results) && nrow(data$results) > 0) {
  as.data.frame(data$results)
} else {
  data.frame(label="No data", category="", status="error",
             latency_ms=NA, note="Checker failed", stringsAsFactors=FALSE)
}

status_badge <- function(s) {
  switch(as.character(s),
    reachable    = "\\textcolor{green!60!black}{\\textbf{OK}}",
    refused      = "\\textcolor{orange}{\\textbf{REFUSED}}",
    timeout      = "\\textcolor{red}{\\textbf{TIMEOUT}}",
    unreachable  = "\\textcolor{red}{\\textbf{UNREACH}}",
    server_error = "\\textcolor{orange}{\\textbf{SRVERR}}",
    error        = "\\textcolor{red}{\\textbf{ERROR}}",
    skip         = "\\textcolor{gray}{SKIP}",
                   "\\textcolor{gray}{UNK}"
  )
}

df$Status_fmt <- sapply(df$status %||% "error", status_badge)
df$Latency    <- ifelse(is.na(df$latency_ms), "—",
                        paste0(round(df$latency_ms, 0), " ms"))
df$note_short  <- trunc_str(df$note,  50)
df$error_short <- trunc_str(df$error, 58)
```

# Executive Summary

```{r summary_table}
summary_df <- data.frame(
  Metric = c("Total Checks", "Reachable", "Blocked / Timeout",
             "Refused (host up, service down)", "Errors"),
  Count  = c(data$total     %||% 0,
             data$reachable %||% 0,
             data$blocked   %||% 0,
             data$refused   %||% 0,
             data$errors    %||% 0),
  stringsAsFactors = FALSE
)
kable(summary_df, booktabs = TRUE, col.names = c("Metric", "Count")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE, position = "left") %>%
  row_spec(which(summary_df$Metric %in% c("Blocked / Timeout", "Errors")),
           bold = TRUE, color = "red")
```

**Generated:** `r data$generated_at %||% "unknown"`

> **Key:** `OK` = TCP/HTTP connection succeeded. `TIMEOUT` = likely firewalled by UF IT.
> `REFUSED` = host up but service not listening. `UNREACH` = no route to host.

\newpage

# Local FPREN Services

```{r local_services}
local_df <- df %>%
  filter(category == "local") %>%
  mutate(Port = as.character(port)) %>%
  select(label, Port, Status_fmt, Latency, note_short) %>%
  rename(Service = label, Status = Status_fmt, Note = note_short)

kable(local_df, booktabs = TRUE, escape = FALSE,
      caption = "Localhost service reachability") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

# UF Network Services

```{r uf_network}
uf_df <- df %>%
  filter(category == "uf_network") %>%
  mutate(Port = as.character(port)) %>%
  select(label, host, Port, Status_fmt, Latency, note_short) %>%
  rename(Service = label, Host = host, Status = Status_fmt, Note = note_short)

kable(uf_df, booktabs = TRUE, escape = FALSE,
      caption = "UF internal network service reachability") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

\newpage

# External APIs & Services

```{r external_apis}
ext_df <- df %>%
  filter(category == "external_api") %>%
  mutate(Port = as.character(port),
         Code = ifelse(is.na(http_code), "—", as.character(http_code))) %>%
  select(label, Port, Status_fmt, Latency, Code, note_short) %>%
  rename(Service = label, Status = Status_fmt, HTTP = Code, Note = note_short)

kable(ext_df, booktabs = TRUE, escape = FALSE,
      caption = "External API reachability from UF VM") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

# Registered SNMP Devices

```{r snmp_devices}
snmp_df <- df %>% filter(category == "snmp_device")

if (nrow(snmp_df) == 0) {
  cat("No SNMP devices are registered to user assets yet.")
} else {
  snmp_tbl <- snmp_df %>%
    mutate(Port = as.character(port)) %>%
    select(label, host, Port, Status_fmt, Latency, note_short) %>%
    rename(Device = label, IP = host, Status = Status_fmt,
           Latency = Latency, `Asset / User` = note_short)
  kable(snmp_tbl, booktabs = TRUE, escape = FALSE,
        caption = "SNMP device reachability (TCP to configured IP:Port)") %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                  full_width = FALSE)
}
```

\newpage

# Firewall / Access Issues

```{r firewall_issues}
blocked <- df %>%
  filter(status %in% c("timeout", "unreachable", "error")) %>%
  mutate(Port = as.character(port)) %>%
  select(label, host, Port, status, error_short, note_short) %>%
  rename(Service = label, Host = host, Status = status,
         `Error Detail` = error_short, Note = note_short)

if (nrow(blocked) == 0) {
  cat("No blocked or unreachable services detected.")
} else {
  kable(blocked, booktabs = TRUE, escape = TRUE,
        caption = "Services that are BLOCKED, timed out, or errored") %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                  full_width = FALSE) %>%
    row_spec(seq_len(nrow(blocked)), color = "red")
}
```

# Recommendations for UF IT

```{r recommendations, results='asis'}
issues <- df %>% filter(status %in% c("timeout", "unreachable"))
if (nrow(issues) == 0) {
  cat("No blocked services detected. All tested endpoints are reachable.\n\n")
} else {
  lines <- sapply(seq_len(nrow(issues)), function(i)
    sprintf("- Open **%s port %s** on VM 128.227.67.234 — *%s*",
            issues$protocol[i], issues$port[i], issues$label[i]))
  cat(paste(lines, collapse = "\n\n"))
  cat("\n\n")
}
cat("*Note: Icecast port 8000 zone streams and Dashboard ports 80/443 are pending UF IT approval per project plan.*")
```
