---
title: "FPREN Connectivity & Accessibility Report"
subtitle: "Port, Service, and API Reachability — UF VM"
date: "`r format(Sys.time(), '%B %d, %Y %I:%M %p %Z')`"
output:
  pdf_document:
    latex_engine: xelatex
    toc: true
    toc_depth: 2
params:
  mongo_uri: "mongodb://localhost:27017/"
  checker_script: "/home/ufuser/Fpren-main/scripts/check_fpren_access.py"
  python_bin: "/home/ufuser/Fpren-main/venv/bin/python3"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(jsonlite)
library(dplyr)
library(knitr)
library(kableExtra)
```

```{r run_checker}
# Run the Python connectivity checker
raw <- tryCatch(
  system2(params$python_bin,
          args    = c(params$checker_script, "--pretty"),
          stdout  = TRUE, stderr = FALSE, timeout = 120),
  error = function(e) NULL
)

if (is.null(raw) || length(raw) == 0) {
  data <- list(results = data.frame(), total = 0,
               reachable = 0, blocked = 0, refused = 0, errors = 0,
               generated_at = "N/A")
} else {
  data <- tryCatch(fromJSON(paste(raw, collapse = "\n")),
                   error = function(e) list(results = data.frame()))
}

df <- if (is.data.frame(data$results) && nrow(data$results) > 0) {
  as.data.frame(data$results)
} else {
  data.frame(label="No data", category="", status="error",
             latency_ms=NA, note="Checker failed", stringsAsFactors=FALSE)
}

# Status colour mapping
status_colour <- function(s) {
  switch(s,
    reachable    = "\\textcolor{green!60!black}{\\textbf{REACHABLE}}",
    refused      = "\\textcolor{orange}{\\textbf{REFUSED}}",
    timeout      = "\\textcolor{red}{\\textbf{TIMEOUT}}",
    unreachable  = "\\textcolor{red}{\\textbf{UNREACHABLE}}",
    server_error = "\\textcolor{orange}{\\textbf{SERVER ERR}}",
    error        = "\\textcolor{red}{\\textbf{ERROR}}",
    skip         = "\\textcolor{gray}{SKIP}",
    "\\textcolor{gray}{UNKNOWN}"
  )
}

df$Status_fmt <- sapply(df$status %||% "error", status_colour)
df$Latency    <- ifelse(is.na(df$latency_ms), "—",
                        paste0(df$latency_ms, " ms"))
```

# Executive Summary

```{r summary_table}
summary_df <- data.frame(
  Metric  = c("Total Checks", "Reachable", "Blocked / Timeout",
              "Refused (host up, service down)", "Errors"),
  Count   = c(data$total    %||% 0,
              data$reachable %||% 0,
              data$blocked   %||% 0,
              data$refused   %||% 0,
              data$errors    %||% 0),
  stringsAsFactors = FALSE
)
kable(summary_df, booktabs = TRUE, col.names = c("Metric","Count")) %>%
  kable_styling(latex_options = c("striped","hold_position"), full_width = FALSE) %>%
  row_spec(which(summary_df$Metric %in% c("Blocked / Timeout","Errors")),
           bold = TRUE, color = "red")
```

**Generated:** `r data$generated_at %||% "unknown"`

> **Interpretation:** TIMEOUT typically means UF IT firewall is blocking the port.
> REFUSED means the host is reachable but the service is not running.
> REACHABLE means a TCP connection was established (or an HTTP 2xx/4xx was returned).

\newpage

# Local FPREN Services

```{r local_services}
local_df <- df %>%
  filter(category == "local") %>%
  select(label, host, port, Status_fmt, Latency, note) %>%
  rename(Service = label, Host = host, Port = port,
         Status = Status_fmt, `Latency` = Latency, Note = note)

kable(local_df, booktabs = TRUE, escape = FALSE,
      caption = "Localhost service reachability") %>%
  kable_styling(latex_options = c("striped","hold_position","scale_down"))
```

# UF Network Services

```{r uf_network}
uf_df <- df %>%
  filter(category == "uf_network") %>%
  select(label, host, port, Status_fmt, Latency, note) %>%
  rename(Service = label, Host = host, Port = port,
         Status = Status_fmt, Latency = Latency, Note = note)

kable(uf_df, booktabs = TRUE, escape = FALSE,
      caption = "UF internal network service reachability") %>%
  kable_styling(latex_options = c("striped","hold_position","scale_down"))
```

# External APIs & Services

```{r external_apis}
ext_df <- df %>%
  filter(category == "external_api") %>%
  select(label, host, port, Status_fmt, Latency, http_code, note) %>%
  rename(Service = label, Host = host, Port = port,
         Status = Status_fmt, Latency = Latency,
         `HTTP Code` = http_code, Note = note)

kable(ext_df, booktabs = TRUE, escape = FALSE,
      caption = "External API reachability from UF VM") %>%
  kable_styling(latex_options = c("striped","hold_position","scale_down"))
```

\newpage

# Registered SNMP Devices

```{r snmp_devices}
snmp_df <- df %>% filter(category == "snmp_device")

if (nrow(snmp_df) == 0) {
  cat("No SNMP devices are registered to user assets yet.")
} else {
  snmp_df <- snmp_df %>%
    select(label, host, port, Status_fmt, Latency, note) %>%
    rename(Device = label, IP = host, Port = port,
           Status = Status_fmt, Latency = Latency, `Asset / User` = note)
  kable(snmp_df, booktabs = TRUE, escape = FALSE,
        caption = "SNMP device reachability (TCP to configured IP:Port)") %>%
    kable_styling(latex_options = c("striped","hold_position","scale_down"))
}
```

# Firewall / Access Issues

```{r firewall_issues}
blocked <- df %>%
  filter(status %in% c("timeout", "unreachable", "error")) %>%
  select(label, host, port, status, error, note) %>%
  rename(Service = label, Host = host, Port = port,
         Status = status, `Error Detail` = error, Note = note)

if (nrow(blocked) == 0) {
  cat("No blocked or unreachable services detected.")
} else {
  kable(blocked, booktabs = TRUE, escape = TRUE,
        caption = "Services that are BLOCKED, timed out, or errored") %>%
    kable_styling(latex_options = c("striped","hold_position","scale_down")) %>%
    row_spec(seq_len(nrow(blocked)), color = "red")
}
```

# Recommendations for UF IT

```{r recommendations}
issues <- df %>% filter(status %in% c("timeout","unreachable"))
cat(paste(
  "Based on this check, the following ports should be requested from UF IT:\n\n",
  paste(
    sapply(seq_len(nrow(issues)), function(i)
      sprintf("  - Open %s port %s to/from the VM (128.227.67.234): %s",
              issues$protocol[i], issues$port[i], issues$label[i])),
    collapse = "\n"
  ),
  if (nrow(issues) == 0) "  No blocked services detected. All tested endpoints are reachable." else "",
  "\n\nNote: Some ports (Icecast 8000, Dashboard 80/443) are awaiting UF IT approval per project plan."
))
```
