---
title: "FPREN Weather Alert Report"
subtitle: "Florida Public Radio Emergency Network — `r params$zone_label`"
date: "Generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`"
geometry: "margin=1in"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: true
    fig_caption: true
    latex_engine: xelatex
    keep_tex: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{xcolor}
  - \definecolor{fprenblue}{RGB}{0, 70, 127}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\textcolor{fprenblue}{\textbf{FPREN}}}
  - \fancyhead[R]{\textcolor{gray}{Emergency Alert Report}}
  - \renewcommand{\headrulewidth}{0.4pt}
params:
  days_back: 7
  zone_label: "All Florida"
  mongo_uri: "mongodb://localhost:27017/"
  severity_filter: "all"
  event_filter: "all"
  date_from: ""
  date_to: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo    = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.width  = 7,
  fig.height = 4,
  fig.align  = "center"
)

library(mongolite)
library(dplyr)
library(tidyr)
library(ggplot2)
library(scales)
library(gridExtra)
library(lubridate)
library(knitr)
library(kableExtra)
library(zoo)

# ── Pull data from MongoDB ───────────────────────────────────────────────────
get_col <- function(collection) {
  tryCatch(
    mongo(collection = collection, db = "weather_rss", url = params$mongo_uri),
    error = function(e) NULL
  )
}

# ── Date range ───────────────────────────────────────────────────────────────
if (nchar(params$date_from) > 0 && nchar(params$date_to) > 0) {
  cutoff     <- as.POSIXct(paste0(params$date_from, "T00:00:00Z"), tz = "UTC")
  cutoff_end <- as.POSIXct(paste0(params$date_to,   "T23:59:59Z"), tz = "UTC")
  date_query <- paste0(
    '{"fetched_at": {"$gte": {"$date": "', format(cutoff, "%Y-%m-%dT%H:%M:%SZ"),
    '"}, "$lte": {"$date": "', format(cutoff_end, "%Y-%m-%dT%H:%M:%SZ"), '"}}}'
  )
} else {
  cutoff     <- Sys.time() - days(params$days_back)
  cutoff_end <- Sys.time()
  date_query <- paste0('{"fetched_at": {"$gte": {"$date": "',
                        format(cutoff, "%Y-%m-%dT%H:%M:%SZ"), '"}}}')
}

col <- get_col("nws_alerts")
alerts_raw <- if (!is.null(col)) {
  tryCatch({
    df <- col$find(
      query  = date_query,
      fields = '{"alert_id":1,"event":1,"headline":1,"severity":1,
                 "area_desc":1,"source":1,"sent":1,"fetched_at":1,
                 "tts_generated":1,"alachua_county":1,"_id":0}'
    )
    col$disconnect()
    df
  }, error = function(e) { col$disconnect(); data.frame() })
} else data.frame()

# ── Apply severity / event filters ───────────────────────────────────────────
if (nrow(alerts_raw) > 0) {
  if (!is.null(params$severity_filter) && params$severity_filter != "all" &&
      nchar(params$severity_filter) > 0) {
    sevs <- trimws(strsplit(params$severity_filter, ",")[[1]])
    alerts_raw <- alerts_raw %>% filter(severity %in% sevs)
  }
  if (!is.null(params$event_filter) && params$event_filter != "all" &&
      nchar(params$event_filter) > 0) {
    evts <- trimws(strsplit(params$event_filter, ",")[[1]])
    alerts_raw <- alerts_raw %>% filter(event %in% evts)
  }
}

# ── Normalise timestamps ──────────────────────────────────────────────────────
if (nrow(alerts_raw) > 0 && "fetched_at" %in% names(alerts_raw)) {
  alerts_raw$fetched_at <- as.POSIXct(alerts_raw$fetched_at, tz = "UTC")
  alerts_raw$date       <- as.Date(alerts_raw$fetched_at, tz = "America/New_York")
  alerts_raw$hour       <- hour(with_tz(alerts_raw$fetched_at, "America/New_York"))
  alerts_raw$weekday    <- weekdays(alerts_raw$date)
  alerts_raw$severity   <- factor(
    alerts_raw$severity,
    levels = c("Extreme","Severe","Moderate","Minor","Unknown"),
    exclude = NULL
  )
}

n_total    <- nrow(alerts_raw)
n_extreme  <- sum(alerts_raw$severity %in% c("Extreme","Severe"), na.rm = TRUE)
n_tts      <- sum(alerts_raw$tts_generated == TRUE, na.rm = TRUE)
n_alachua  <- sum(alerts_raw$alachua_county == TRUE, na.rm = TRUE)

period_label <- paste0(
  format(cutoff, "%b %d"), " – ", format(Sys.time(), "%b %d, %Y")
)

sev_colors <- c(
  Extreme  = "#c0392b",
  Severe   = "#e67e22",
  Moderate = "#f1c40f",
  Minor    = "#2ecc71",
  Unknown  = "#95a5a6"
)
```

\newpage

# Executive Summary

**Report Period:** `r period_label` (`r params$days_back` days)
**Coverage Zone:** `r params$zone_label`
**Data Source:** NOAA/NWS via FPREN MongoDB

---

```{r summary-boxes, results='asis'}
cat(paste0(
  "| Metric | Value |\n",
  "|--------|-------|\n",
  "| Total Alerts | **", n_total, "** |\n",
  "| Extreme / Severe | **", n_extreme, "** |\n",
  "| Audio (TTS) Generated | **", n_tts, "** |\n",
  "| Alachua County | **", n_alachua, "** |\n",
  "| Avg Alerts / Day | **", round(n_total / max(params$days_back, 1), 1), "** |\n"
))
```

```{r no-data-check, results='asis'}
if (n_total == 0) {
  cat("\n> **No alerts were recorded during this period.**\n")
  knitr::knit_exit()
}
```

\newpage

# Alert Volume Over Time

```{r daily-volume, fig.cap="Daily alert count for the reporting period."}
daily <- alerts_raw %>%
  count(date, severity) %>%
  complete(date = seq(min(date), max(date), by = "day"),
           severity, fill = list(n = 0))

ggplot(daily, aes(x = date, y = n, fill = severity)) +
  geom_col(position = "stack", width = 0.8) +
  scale_fill_manual(values = sev_colors, na.value = "#95a5a6",
                    name = "Severity") +
  scale_x_date(date_labels = "%b %d", date_breaks = "1 day") +
  scale_y_continuous(breaks = scales::pretty_breaks()) +
  labs(x = NULL, y = "Alert Count",
       title = "Daily Alert Volume by Severity") +
  theme_minimal(base_size = 11) +
  theme(
    axis.text.x  = element_text(angle = 45, hjust = 1),
    panel.grid.minor = element_blank(),
    legend.position  = "right"
  )
```

```{r hourly-heatmap, fig.cap="Alert activity by hour of day (Eastern Time)."}
if (nrow(alerts_raw) > 0 && "hour" %in% names(alerts_raw)) {
  hourly <- alerts_raw %>% count(hour) %>%
    complete(hour = 0:23, fill = list(n = 0))

  ggplot(hourly, aes(x = hour, y = n)) +
    geom_col(fill = "#2980b9", width = 0.85) +
    scale_x_continuous(breaks = seq(0, 23, 3),
                       labels = sprintf("%02d:00", seq(0, 23, 3))) +
    scale_y_continuous(breaks = scales::pretty_breaks()) +
    labs(x = "Hour (ET)", y = "Alert Count",
         title = "Alerts by Hour of Day") +
    theme_minimal(base_size = 11) +
    theme(panel.grid.minor = element_blank())
}
```

\newpage

# Severity Distribution

```{r severity-charts, fig.width=7, fig.height=3.5, fig.cap="Alert severity breakdown."}
sev_counts <- alerts_raw %>%
  count(severity, .drop = FALSE) %>%
  filter(n > 0) %>%
  arrange(desc(n))

p1 <- ggplot(sev_counts, aes(x = reorder(severity, n), y = n, fill = severity)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = n), hjust = -0.2, size = 3.5) +
  scale_fill_manual(values = sev_colors, na.value = "#95a5a6") +
  coord_flip() +
  labs(x = NULL, y = "Count", title = "By Severity") +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank())

p2 <- ggplot(sev_counts, aes(x = "", y = n, fill = severity)) +
  geom_col(width = 1, color = "white") +
  coord_polar("y") +
  scale_fill_manual(values = sev_colors, na.value = "#95a5a6", name = NULL) +
  geom_text(aes(label = paste0(round(n/sum(n)*100), "%")),
            position = position_stack(vjust = 0.5), size = 3, color = "white") +
  labs(title = "Share") +
  theme_void(base_size = 10) +
  theme(legend.position = "right")

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

\newpage

# Top Alert Types

```{r event-types, fig.cap="Most frequent NWS alert event types."}
top_events <- alerts_raw %>%
  count(event, sort = TRUE) %>%
  slice_head(n = 15)

ggplot(top_events, aes(x = reorder(event, n), y = n)) +
  geom_col(fill = "#2980b9") +
  geom_text(aes(label = n), hjust = -0.2, size = 3) +
  coord_flip() +
  labs(x = NULL, y = "Count", title = "Top 15 Alert Event Types") +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank())
```

```{r event-table}
top_events %>%
  rename(`Event Type` = event, Count = n) %>%
  mutate(`% of Total` = paste0(round(Count / n_total * 100, 1), "%")) %>%
  kable(booktabs = TRUE, align = c("l","r","r"),
        caption = "Alert frequency by event type") %>%
  kable_styling(latex_options = c("striped","hold_position"), font_size = 9)
```

\newpage

# Statistical Analysis

## Alert Arrival Rate (Poisson Model)

```{r poisson}
daily_counts <- alerts_raw %>%
  count(date) %>%
  complete(date = seq(min(date), max(date), by = "day"), fill = list(n = 0))

lambda_hat  <- mean(daily_counts$n)
variance    <- var(daily_counts$n)
dispersion  <- if (is.na(variance) || lambda_hat == 0) NA_real_ else variance / lambda_hat

disp_label <- if (is.na(dispersion)) " — *insufficient data for dispersion*" else if (dispersion > 1.5) " — *overdispersed (bursty pattern)*" else if (dispersion < 0.5) " — *underdispersed (regular pattern)*" else " — *consistent with Poisson process*"

cat(paste0(
  "**Mean daily alert rate (λ):** ", round(lambda_hat, 2), " alerts/day\n\n",
  "**Variance:** ", ifelse(is.na(variance), "N/A (single day)", round(variance, 2)), "\n\n",
  "**Dispersion index (var/mean):** ", ifelse(is.na(dispersion), "N/A", round(dispersion, 2)),
  disp_label,
  "\n\n",
  "**95% CI for daily rate:** [",
  round(qpois(0.025, lambda_hat), 0), ", ",
  round(qpois(0.975, lambda_hat), 0), "] alerts/day\n"
))
```

## Severity Trend Over Time

```{r severity-trend, fig.cap="Rolling 3-day average of high-severity (Extreme + Severe) alerts."}
if (params$days_back >= 5) {
  trend <- alerts_raw %>%
    mutate(high_sev = severity %in% c("Extreme","Severe")) %>%
    count(date, high_sev) %>%
    filter(high_sev) %>%
    complete(date = seq(min(alerts_raw$date), max(alerts_raw$date), by = "day"),
             fill = list(n = 0, high_sev = TRUE)) %>%
    arrange(date) %>%
    mutate(rolling_avg = zoo::rollmean(n, k = min(3, n()), fill = NA, align = "right"))

  ggplot(trend, aes(x = date)) +
    geom_col(aes(y = n), fill = "#e74c3c", alpha = 0.4, width = 0.8) +
    geom_line(aes(y = rolling_avg), color = "#c0392b", linewidth = 1,
              na.rm = TRUE) +
    scale_x_date(date_labels = "%b %d", date_breaks = "1 day") +
    scale_y_continuous(breaks = scales::pretty_breaks()) +
    labs(x = NULL, y = "Count",
         title = "Extreme/Severe Alerts - Daily Count + 3-Day Rolling Average",
         caption = "Red bars = daily count; line = 3-day rolling mean") +
    theme_minimal(base_size = 10) +
    theme(axis.text.x = element_text(angle = 45, hjust = 1),
          panel.grid.minor = element_blank())
} else {
  cat("_Trend analysis requires at least 5 days of data._")
}
```

## Day-of-Week Pattern

```{r dow, fig.cap="Alert frequency by day of week."}
dow_order <- c("Sunday","Monday","Tuesday","Wednesday","Thursday","Friday","Saturday")
dow_counts <- alerts_raw %>%
  mutate(weekday = factor(weekday, levels = dow_order)) %>%
  count(weekday, .drop = FALSE)

ggplot(dow_counts, aes(x = weekday, y = n, fill = n)) +
  geom_col(show.legend = FALSE) +
  geom_text(aes(label = n), vjust = -0.4, size = 3.5) +
  scale_fill_gradient(low = "#aed6f1", high = "#1a5276") +
  labs(x = NULL, y = "Alert Count", title = "Alerts by Day of Week") +
  theme_minimal(base_size = 10) +
  theme(panel.grid.minor = element_blank())
```

\newpage

# Top Affected Areas

```{r top-areas}
area_counts <- alerts_raw %>%
  tidyr::separate_rows(area_desc, sep = ";\\s*") %>%
  mutate(area_desc = trimws(area_desc)) %>%
  filter(nchar(area_desc) > 2) %>%
  count(area_desc, sort = TRUE) %>%
  slice_head(n = 20)

area_counts %>%
  rename(Area = area_desc, `Alert Count` = n) %>%
  kable(booktabs = TRUE, longtable = TRUE, align = c("l","r"),
        caption = "Top 20 most-alerted geographic areas") %>%
  kable_styling(latex_options = c("striped","hold_position","repeat_header"),
                font_size = 9)
```

\newpage

# Audio Generation Summary

```{r tts-summary}
tts_rate <- if (n_total > 0) round(n_tts / n_total * 100, 1) else 0

cat(paste0(
  "**Alerts with TTS audio generated:** ", n_tts, " of ", n_total,
  " (", tts_rate, "%)\n\n"
))

if ("tts_generated" %in% names(alerts_raw)) {
  tts_by_sev <- alerts_raw %>%
    group_by(severity) %>%
    summarise(
      Total     = n(),
      TTS_Done  = sum(tts_generated == TRUE, na.rm = TRUE),
      Rate_Pct  = paste0(round(TTS_Done / Total * 100, 1), "%"),
      .groups   = "drop"
    ) %>%
    arrange(desc(Total))

  tts_by_sev %>%
    rename(Severity = severity, `TTS Done` = TTS_Done, `Rate` = Rate_Pct) %>%
    kable(booktabs = TRUE, align = c("l","r","r","r"),
          caption = "TTS generation rate by severity") %>%
    kable_styling(latex_options = c("striped","hold_position"), font_size = 9)
}
```

---

*Report generated by FPREN R reporting system. Data sourced from NOAA/NWS via MongoDB.*
*RStudio Server: `r Sys.info()[["nodename"]]` | R `r R.version.string`*
