---
title: "FPREN Traffic Analysis Report"
subtitle: "Florida Public Radio Emergency Network — FL511 Traffic Incidents"
date: "Generated `r format(Sys.time(), '%B %d, %Y at %I:%M %p')`"
geometry: "margin=1in"
output:
  pdf_document:
    toc: true
    toc_depth: 2
    number_sections: false
    latex_engine: xelatex
    keep_tex: false
header-includes:
  - \usepackage{booktabs}
  - \usepackage{xcolor}
  - \usepackage{longtable}
  - \usepackage{array}
  - \definecolor{fprenblue}{RGB}{0, 70, 127}
  - \definecolor{majorred}{RGB}{192, 57, 43}
  - \definecolor{intermorange}{RGB}{230, 126, 34}
  - \definecolor{minoryellow}{RGB}{243, 156, 18}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \fancyhead[L]{\textcolor{fprenblue}{\textbf{FPREN}}}
  - \fancyhead[C]{\textcolor{fprenblue}{Traffic Analysis Report}}
  - \fancyhead[R]{\textcolor{gray}{Florida Public Radio Emergency Network}}
  - \renewcommand{\headrulewidth}{0.4pt}
params:
  data_rds: ""
  filters:  "No filters applied"
  date:     ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.width = 7, fig.height = 4)
library(dplyr)
library(ggplot2)
library(knitr)
library(kableExtra)

df <- readRDS(params$data_rds)
```

\textcolor{fprenblue}{\textbf{Florida Public Radio Emergency Network}} \hfill \textcolor{gray}{Automated Traffic Report}

\vspace{4pt}
\hrule
\vspace{8pt}

**Active Filters:** `r params$filters`

**Report Date:** `r format(Sys.Date(), "%B %d, %Y")`

**Total Incidents in Report:** `r nrow(df)`

---

## Summary Statistics

```{r summary-boxes}
total     <- nrow(df)
n_major   <- sum(df$severity %in% c("Major","Intermediate"), na.rm=TRUE)
n_closure <- sum(df$is_full_closure == TRUE, na.rm=TRUE)
n_county  <- length(unique(df$county[!is.na(df$county)]))

summary_df <- data.frame(
  Metric = c("Total Incidents","Major / Intermediate","Full Closures","Counties Affected"),
  Count  = c(total, n_major, n_closure, n_county)
)
kable(summary_df, booktabs=TRUE, col.names=c("Metric","Count"),
      caption="Incident Summary") %>%
  kable_styling(latex_options=c("hold_position"), full_width=FALSE) %>%
  column_spec(2, bold=TRUE)
```

---

## Incidents by Road (Top 20)

```{r road-chart, fig.height=5}
road_counts <- df %>%
  filter(!is.na(road), road != "") %>%
  count(road, sort=TRUE) %>%
  slice_head(n=20) %>%
  mutate(road = reorder(road, n))

ggplot(road_counts, aes(x=n, y=road)) +
  geom_col(fill="#3498db") +
  geom_text(aes(label=n), hjust=-0.2, size=2.8) +
  labs(x="Incidents", y=NULL, title="Top 20 Roads by Incident Count") +
  theme_minimal(base_size=10) +
  theme(plot.title=element_text(color="#00467f", face="bold"),
        panel.grid.major.y=element_blank()) +
  scale_x_continuous(expand=expansion(mult=c(0,0.12)))
```

---

## Incident Type Breakdown

```{r type-chart, fig.height=3.5}
type_counts <- df %>%
  filter(!is.na(type), type != "") %>%
  count(type, sort=TRUE) %>%
  mutate(pct = round(n/sum(n)*100,1),
         label = paste0(type, "\n", n, " (", pct, "%)"))

ggplot(type_counts, aes(x="", y=n, fill=type)) +
  geom_col(width=1, color="white") +
  coord_polar("y") +
  labs(fill="Type", title="Incidents by Type") +
  theme_void(base_size=9) +
  theme(plot.title=element_text(color="#00467f", face="bold", hjust=0.5),
        legend.text=element_text(size=7))
```

---

## Incidents by County (Top 25)

```{r county-chart, fig.height=5}
county_counts <- df %>%
  filter(!is.na(county), county != "") %>%
  count(county, sort=TRUE) %>%
  slice_head(n=25) %>%
  mutate(county = reorder(county, n))

ggplot(county_counts, aes(x=n, y=county, fill=n)) +
  geom_col() +
  geom_text(aes(label=n), hjust=-0.2, size=2.8) +
  scale_fill_gradient(low="#fecc5c", high="#bd0026", guide="none") +
  labs(x="Incidents", y=NULL, title="Top 25 Counties by Incident Count") +
  theme_minimal(base_size=10) +
  theme(plot.title=element_text(color="#00467f", face="bold"),
        panel.grid.major.y=element_blank()) +
  scale_x_continuous(expand=expansion(mult=c(0,0.12)))
```

---

## Severity Breakdown by Road (Top 15)

```{r severity-chart, fig.height=5}
sev_counts <- df %>%
  filter(!is.na(road), road != "", !is.na(severity)) %>%
  count(road, severity) %>%
  group_by(road) %>%
  mutate(total=sum(n)) %>%
  ungroup() %>%
  filter(dense_rank(desc(total)) <= 15) %>%
  mutate(road = reorder(road, total),
         severity = factor(severity, levels=c("Major","Intermediate","Minor","N/A")))

sev_colors <- c(Major="#e74c3c", Intermediate="#e67e22", Minor="#f1c40f", `N/A`="#95a5a6")

ggplot(sev_counts, aes(x=n, y=road, fill=severity)) +
  geom_col(position="stack") +
  scale_fill_manual(values=sev_colors) +
  labs(x="Incidents", y=NULL, fill="Severity",
       title="Severity Distribution - Top 15 Roads") +
  theme_minimal(base_size=10) +
  theme(plot.title=element_text(color="#00467f", face="bold"),
        panel.grid.major.y=element_blank())
```

---

## Full Closures

```{r closures-table}
closures <- df %>%
  filter(is_full_closure == TRUE) %>%
  mutate(description = substr(gsub("<[^>]+>","",description), 1, 120)) %>%
  select(any_of(c("severity","county","road","direction","type","description","last_updated"))) %>%
  rename_with(~c("Severity","County","Road","Direction","Type","Description","Last Updated")[seq_along(.)], everything())

if (nrow(closures) == 0) {
  cat("No full closures in current data set.\n")
} else {
  kable(closures, booktabs=TRUE, longtable=TRUE,
        caption=paste0("Full Closures (", nrow(closures), " total)")) %>%
    kable_styling(latex_options=c("hold_position"), font_size=8) %>%
    column_spec(1, width="1.5cm") %>%
    column_spec(2, width="2cm") %>%
    column_spec(3, width="2.5cm") %>%
    column_spec(4, width="1.5cm") %>%
    column_spec(5, width="2cm") %>%
    column_spec(6, width="5cm")
}
```

---

## Incident Detail Table

```{r detail-table}
MAX_ROWS <- 250
detail_all <- df %>%
  select(any_of(c("severity","county","road","direction","type",
                   "is_full_closure","dot_district","last_updated"))) %>%
  rename_with(~c("Severity","County","Road","Direction","Type",
                  "Full Closure","District","Last Updated")[seq_along(.)], everything()) %>%
  arrange(desc(Severity), County)

truncated <- nrow(detail_all) > MAX_ROWS
detail    <- head(detail_all, MAX_ROWS)

cap <- paste0("Incident Detail — ", nrow(detail), " of ", nrow(detail_all), " records",
              if (truncated) paste0(" (top ", MAX_ROWS, " shown; download CSV for full data)") else "")

kable(detail, booktabs=TRUE, longtable=TRUE, caption=cap) %>%
  kable_styling(latex_options=c("hold_position"), font_size=7) %>%
  column_spec(1, bold=TRUE, width="1.5cm") %>%
  column_spec(2, width="2cm") %>%
  column_spec(3, width="3cm") %>%
  column_spec(4, width="1.5cm") %>%
  column_spec(5, width="2.5cm") %>%
  column_spec(6, width="1.2cm") %>%
  column_spec(7, width="1.2cm") %>%
  column_spec(8, width="2.5cm")
```

---

\vspace{12pt}
\hrule
\vspace{4pt}
\small\textcolor{gray}{Generated by FPREN — Florida Public Radio Emergency Network | Powered by FL511 data | `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`}
